### 2020-10-01 mnras_template.tex

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[letters, usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.

\title[V4046\,Sgr high-resolution ALMA observations]{V4046\,Sgr high-resolution 1.3\,mm continuum ALMA observations: a disc with a thin ring}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. Martinez Brunner et al.]{
R. Martinez-Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Chile\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2020}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
   %%%%context
    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that has a gas-rich circumbinary disc.
    We report on new $\sim20$\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure. We use a parametric a radiative transfer model of the circumbinary disc, computed with \textsc{radmc3d} to interpret the available data, including the spectral-energy-distribution, in terms of a physical model. In addition, we explore decompositions of the imaging data in polar coordinates to better constrain the disc radial structure. 
    We report a two ringed structure for the millimetre-size dust population with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au. This ring is the finest reported so far in a gas rich protoplanetary disc. The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au. The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au.The RT model reproduces accurately the available data. We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations. The shadow of the secondary reported previously from the scattered-light data is also reproduced by the RT model. The DPI image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with rather large dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains. Using the parametric model scale height as an estimated height, we found that the thin inner ring is stable. Deeper ALMA observations may confirm the lopsided 5\,au ring.

%briefly describe the aims, methods, and main results
%single paragraph not more than 250 words
%No references should appear
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
 protoplanetary discs -- submillimetre: planetary systems -- radiative transfer
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction} \label{sec:Introduction}

Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with The Atacama Large Millimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources. This report is part of a survey of discs around T-Tauri Stars (DARTSS - ref Avenhaus, Perez et al in pret). Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr, which is a remarkable system where we can observe fundamental processes associated with disc evolution.

V4046 Sagittarii (Sgr) is is a double-lined spectroscopic binary of a nearly equal-mass pair of K-type stars (K5 and K7) with masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}. The V4046\,Sgr system locate at 72.41$\pm$0.34\,pc away \citep{Gaia}, and is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, fixing its age at 23$\pm$3\,Myr \citep{Mamajek_2014}. V4046\,Sgr binary system is surrounded by a massive ($\sim$0.1\,M$_{\sun}$), gas-rich disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}. The disc has a vast variety of molecules with a detailed subarcsecond ALMA molecular line imaging study by \citet{Kastner_2018}. The chemical structure is composed of CO and HCN that display centrally peaked morphologies, a sequence of sharp and diffuse rings of complex nitrile group molecules (HC$_3$N, CH$_3$CN), deuterated molecules (DCN, DCO$^+$), hydrocarbons (C$_2$H) and others like N$_2$H$^+$, H$_2$CO.

To analyse the new ALMA data, we aim to reproduce the disc through a parametric model ran with the radiative transfer code \textsc{radmc3d} \citep{Dullemond_2012} so that the model would agree with the ALMA observation, a previous SPHERE-IRDIS observation and the Spectral Energy Distribution (SED). With the model representation of the dust density distribution and combined with a decomposition in polar coordinates of the ALMA image we can have better approximations of the radial structure of the disc. It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grains disc.

In the following sections, first we describe the new 1.3\,mm continuum observation alongside with a SPHERE-IRDIS \textit{H}-band image (Section \ref{sec:Observations}), present the structure of the parametric model used to simulate the disc (Section \ref{sec:model}), comment on the results of the comparison of the model with the data and a discussion of the main results (Section \ref{sec:results}). Finally, we share our main conclusions in Section \ref{sec:Conclusions}.

\section{Observations} \label{sec:Observations}

Disc structures can be explored by means of comparing mm continuum and scattered light images. These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered light accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane. By comparing both we can determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.

New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S.. These were taken in the context of a larger survey for 14 optically visible TTauri discs at $\sim$50\,mas resolution. The survey simultaneously mapped 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz). In this work we focus exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs05$.

For this investigation we made use of previous polarimetric image (at 1.65$\micron$) taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument. A complete description of these image and all about data reduction was reported in \citet{Avenhaus_2018}.

For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the \textsc{uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} we can super-resolve the clean beam, obtaining an effective angular resolution $\sim$2-3 times higher than in the clean image with natural weights. The model obtains this higher resolution through fitting the data using Chi-squared minimisation. Here we adopted a pure $\chi ^2$ model image. The resulting \textsc{uvmem} image shown in Fig. \ref{fig:two} exhibits previously unseen substructure of the disc. This unique high-definition image reveals that the disc features a two-ring structure for the large grain dust with a broad gap between the rings. The wide and brighter outer ring has been observed in previous occasions, but the thin and weak inner ring has never seen before (\citet{Ru_z_Rodr_guez_2019} anticipated its existence). The outer ring has its peak intensity at $\sim$30\,au and reaches out to $\sim$60\,au. Additionally, we can observe that there is a surface brightness break at $\sim$35\,au, another feature that has never been considered.

\begin{figure*}
	\includegraphics[width=\textwidth]{hot_two_E.pdf}
    \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6  observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc). Top right panel: 1.3\,mm continuum \textsc{uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs05$. The inset displays a enlarged view of the central emission, the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The yellow ellipse shows the size of the simulated beam: $ 0\farcs04 \, \times \, 0\farcs05$. For all the images in the figure the colour scale is linear.}

    \label{fig:two}
\end{figure*}

The inner ring is surprisingly narrow, and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig. \ref{fig:two}). The ring width can be measured in polar coordinates, following the determination of the inner ring centre and orientation. We minimised the dispersion of the disc radial profiles, from 6\,au to 19\,au (aiming for the inner ring) for a PA of 74.6\,$\degr$, an inclination of 33.9\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.

Assuming a Gaussian dust inner ring, we obtained the mean width and the location of the ring by finding for each azimuth the Gaussian intensity profile that best describes the ring. This gave us a FWHM of 4.17$\pm$0.94\,au and that it is located at 13.46$\pm$0.43\,au from the stars (See Fig. \ref{fig:polarring}). As we are using the \textsc{uvmem} model image and the effective angular resolution is $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs05$), these measurements only gives as an upper limit of the real width.

Doing one more time the minimisation of the dispersion of the disc radial profiles, but this time aiming for the outer ring from 20\,au to 70\,au, for a PA of 76.8\,$\degr$, with an inclination of 34.0\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars, we can compare the measured location of the inner ring according with this parameters versus to the location obtained before. The deviation is shown in Fig. \ref{fig:polarring} and is not trivial since it depend on a few parameters such as the different inclinations of the rings, the difference in position angle and the small shifts of the centres relative to the stars. Those parameters play an important role, but a possible small difference in eccentricities between the inner and the outer ring could also help explain this deviation between the two measurements. ***

Interestingly, the ALMA images also detects faint the 1.3\,mm continuum near the stellar positions (See the inset in Fig. \ref{fig:two}). Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains. This dust structure is at a distance of only $\sim0\farcs02$ from the binary system.

The scattered light image shown in Fig. \ref{fig:two} reveals the presence of a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01 and 24.62$\pm$0.08\,au with a small gap between them at $\sim$20\,au. The observed second ring might correspond to the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.

\citet{dOrazi} also measured the binary phase in the scattered light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise. We can then calculate the binary phase at the time of the ALMA observation and it was at $\phi=$13\,$\degr$. There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained due to the slower cooling of larger grains (cite Casassus?).

\begin{figure}
    \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
    \caption{(a) Polar decomposition of the 1.3\,mm continuum image showing the centres (solid line) of Gaussian fits and the measured FWHM (blue region between the dotted lines) of the inner thin ring for each azimuthal angle. This was obtained centring the \textsc{uvmem} image optimising for the outer ring. (b) Shows the measured location of the inner ring, where the orange line represents the centres of the fitted Gaussian profile obtained in the first panel and blue line represents the same but obtained centring the \textsc{uvmem} image optimising for the inner ring.}
    \label{fig:polarring}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images. The grey shaded area represents the inner working angle of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
    \label{fig:radprofiles}
\end{figure}

\section{Parametric radiative transfer model} \label{sec:model}

To search for a possible model that could explain the available data, we perform radiative transfer modelling with \textsc{radmc3d} \citep{Dullemond_2012}. Here we describe a 3D modelling framework for constructing disc structures given some parameters to characterise it. The model environment is similar to the one used by \citet{2018MNRAS.477.5104C} for DoAr 44. Through trial and error, we look for a set of values for the parameters that can define a model that correctly fits the available data.

For the representation of the stars we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with  T$_{\mathrm{eff},1}=$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2}=$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}}= -$9.3$\pm$0.3\,Myr$^{-1}$ for both cases. The stars were placed with a separation of 0.041\,au and arranged with a 30\,$\degr$ rotation to mach the shadows reported by \citet{dOrazi}.

Recreating the complex radial and vertical structure of the V4046\,Sgr disc is not an easy task. We choose to build the model by thinking the components of the disc separately and then unite them as a whole. Given the observations, we consider that a correct approach for this disc is using two different dust populations: larger grains that are vertically settled and dominates the disc mass and a less-abundant population of smaller grains that are distributed to larger heights from the mid-plane. As the gas and the small-dust population are coupled, it is important to consider the gas in the modelling process, but we are not predicting line emissions.

Assuming a three dimensional model in a spherical reference frame with coordinates (r, $\theta$, $\phi$), gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \text{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right].
\end{equation}
Where $\delta(r)$ is a parameter that indicates the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ been the surface density profile. $\Sigma(r)$ is defined by
\begin{equation}
  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \text{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used a fixed $\gamma$ = 1, a typical value for discs \citep{Andrews_2009,Andrews_2010}.

We define the parametric scale height profiles for the gas and for each dust population as \begin{equation}
    \label{scale}
  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
\end{equation}
where $H_o$ is the scale height at r = $r_o$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. For the gas and the micron-sized grains $\chi$ = 1 and for the millimetre-size dust population, as \citet{Rosenfeld_2013}, we assign a fixed $\chi$ = 1/2 for simplicity.

The small-dust density distribution follows the same behaviour as the gas but with different scaling factors: the dust-to-gas ratio ($\zeta$ = 0.047 as \citet{Rosenfeld_2013}), the mass fraction between small and large dust particles ($f_{\mathrm{mass}}$) and a $\delta(r)$ factor for fine tuning that depends on the radius. So it is
\begin{equation}
\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{mass}} \, \delta(r) \: \zeta .
\end{equation}

Since the large-dust grains are less coupled to the gas, their distribution has some important differences. We leave a large inner cavity and added another scaling factor (or filter) to generate the larger gap between the rings. For the inner ring we use the same profile as the gas but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a sum of an exponential correction with a Gaussian function and, between 32 and 34.5\,au, in an effort to recreate the break seen in the profile, we chose a different value for $\gamma$ = -8. Then we have

\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \text{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \text{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

Also for both dust populations, the inner part of the outer ring follows a different behaviour. To model that parts we multiplied by an additional factor $\epsilon(r)$
\begin{equation}
    \epsilon(r) = \delta +  (1 - \delta) \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
\end{equation}
where $\delta=10^{-4}$ and $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring. This parameter allow us to model a smoother inner wall of the outer ring.

The two different populations of dust grains vary in size, the small grains range from  0.4 to 1.5\,$\micron$ and the large dust grains range from 0.4\,$\micron$ to 10\,mm. For absorption and opacities of dust populations we assume a typical ISM mineralogical composition, containing 70\% silicate and 30\% graphite.

In an effort to obtain a similar asymmetry as the one observed in the DPI image, the simulated image at 1.65\,$\micron$ had to be taken using a special grain size distribution. Our approach was using a Gaussian size distribution centred at 0.4\,$\micron$, smearing out the grain size by 30\% in both directions and using 20 grain size samples in that range.

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
    \caption{Top panel shows the surface density profiles for the gas, the large and small grain populations. Bottom panel shows the scale height $h(r)$ as a function of polar radius. The dashed lines crossing both panels are the radii that confine the structures.}
    \label{fig:profiles}
\end{figure}

The final structure of the parametric model goes as Fig. \ref{fig:profiles} shows. The inner radius of the model grid was set to 0.1\,au and an otter radius of 115\,au, large enough for the dust disc to become undetectable.

The dust begins at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}. For the small dust grains, we propose a three ringed structure. The innermost ring of the model is located from 5 to 8\,au ,this ring is not present in the observations but was added for having a better SED fit. Then follows the two observed rings: the first goes from 12 to 19.5\,au and, with a 1\,au-wide gap between them, the outer ring goes from 20.5\,au and has its maximum density peak at 25\,au. The small-dust density then then fades as the radius increases.

On the other hand, in order to reproduce the two ringed observed morphology of the millimetre continuum emission we required a model that has its large-dust grain population distributed with a wide central cavity (r = 12.3\,au), a narrow 2.6\,au-wide inner ring followed by a gap of 8.2\,au that separates both rings and then an outer ring that goes from 23\,au and has it density peak at 27.3\,au. This last ring has a break between 32 and 34.5\,au and then reaches out to 57\,au.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. For that matter, we used two different flaring index $\psi$ for our model. The separation between the two values was set at $r$ = 19\,au with values of 0.2 and 0.5 for the inner part and the outer part respectively. Also, the scale height is calculated using $H_o$ = 0.045 and $r_0$ = 19.5\,au.

We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section \ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A. = 74.6\,$\degr$. Finally, we set the distance at d = 72.4\,pc \citep{Gaia}.

\section{Model results and discussion} \label{sec:results}

Our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model
are shown in Fig. \ref{fig:two} and Fig. \ref{fig:SED} respectively.

The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations displaying a two ringed disc, where the innermost small-dust ring of the parametric model hides under the artificial coronagraph. The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains. Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the Sphere-IRDIS image.

The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation. The model reproduced the two rings that are present in the observation: the faint inner ring and the outer brighter one. The outer ring has an intensity peak at $\sim$30\,au and a break present at $\sim$35\,au.

As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner ring. Accordingly, taking the parametric model values for the large-dust inner ring we can have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 4\,M$_{\earth}$.

As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring can be analysed comparing its height to its radial extent. For a ring to be stable and long-lived its horizontal dimension can not be less than its vertical height. Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of the inner ring (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable and the disc is capable of supporting a thin ring as this one.

Fig. \ref{fig:SED} shows the SED constructed from the model compared to the photometry data available in the literature in \citet{Jensen_97} and online in \textsc{vizier} and \textsc{diana}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum. From the similarity between the data and the resulting SED of the model we confirm that there has to be a small-grain population close to the stars down to 0.3\,au. The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit, this proposed ring has not been observed. The unexpected central emission in the 1.3\,mm continuum image could be part of this inner ring and, as it is asymmetric, the ring could be lopsided.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.png}
    \caption{The SED (black points and solid red curve) compared with the model (blue). The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.}
    \label{fig:SED}
\end{figure}

\section{Conclusions} \label{sec:Conclusions}

New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr reveals new information about its substructure. Using a radiative transfer model, a preexisting scattered light observation and decompositions in polar coordinates of the computed \textsc{uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.

The key conclusions of our analysis are as follows.
\begin{itemize}
  \item We report a narrow inner ring for the 1.3\,mm continuum at $r$ = 13.46$\pm$0.43\,au and has an estimated width of 4.17$\pm$0.94\,au. The location of this ring is similar to the inner ring observed in the scattered light image, this reveals that the ring includes a considerable mass of millimetre-sized grains of around 4\,M$_{\earth}$. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.

  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.

  %\item The inner ring may not be totally resolved as its width is comparable to the beam size. Future observation with smaller beams sizes could give an answer on the real radial extent of the ring.

  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.

  \item As our parametric model accounts for the SED of the system, the disc requires the existence of a sub-micron dust population close (<5\,au) to the stars. We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains that lies under the coronagraph of the SPHERE images. Additionally, the weak central emission at 1.3\,mm could be part of this ring.

\end{itemize}

Finally, we encourage additional detailed analysis and more modelling that could give some explanations of the substructures present on the disc. Higher resolution observations of radio continuum may provide the opportunity to make better measurements of the rings radial extension. For future radiative transfer models, it might be worth adding gas, using different inclinations for the inner and outer disc and implementing hydrodynamic simulations too, especially to try to unravel the mystery of how the inner ring is so thin an stable.

\section*{Acknowledgements}

Try to keep it short.

\section*{Data Availability}

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{bibtex} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2020-10-02 mnras_template.tex
Add files via upload

@@
 In addition, we explore decompositions of the imaging data in polar coordinates to better constrain the disc radial structure.
-    We report a two ringed structure for the millimetre-size dust population with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au.
+    We report a two ringed structure for the millimetre-size dust population with a narrow, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au. 
     This ring is the finest reported so far in a gas rich protoplanetary disc. 
-The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au.
-The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au.The RT model reproduces accurately the available data.
-We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations.
-The shadow of the secondary reported previously from the scattered-light data is also reproduced by the RT model.
-The DPI image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with rather large dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains.
+    The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au. The radial profile of the outer ring exhibits an intriguing break at $\sim$35\,au. 
+    %The RT model reproduces accurately the available data.
+    %We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations. 
+    %The shadow of the secondary reported previously from the scattered-light data is also reproduced by the RT model. 
+    %The DPI image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with rather large dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains. 
     Using the parametric model scale height as an estimated height, we found that the thin inner ring is stable.
-Deeper ALMA observations may confirm the lopsided 5\,au ring.
+    %Deeper ALMA observations may confirm the lopsided 5\,au ring.
 
@@
 
-Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with The Atacama Large Millimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
+Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
 This report is part of a survey of discs around T-Tauri Stars (DARTSS - ref Avenhaus, Perez et al in pret).
@@
 V4046 Sagittarii (Sgr) is is a double-lined spectroscopic binary of a nearly equal-mass pair of K-type stars (K5 and K7) with masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}.
-The V4046\,Sgr system locate at 72.41$\pm$0.34\,pc away \citep{Gaia}, and is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, fixing its age at 23$\pm$3\,Myr \citep{Mamajek_2014}.
+The V4046\,Sgr system locate at 72.41$\pm$0.34\,pc \citep{Gaia}, and is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, fixing its age at 23$\pm$3\,Myr \citep{Mamajek_2014}.
 V4046\,Sgr binary system is surrounded by a massive ($\sim$0.1\,M$_{\sun}$), gas-rich disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}.
@@
 \citet{dOrazi} also measured the binary phase in the scattered light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
-We can then calculate the binary phase at the time of the ALMA observation and it was at $\phi=$13\,$\degr$.
+We can then calculate the binary phase at the time of the ALMA observation at $\phi=$13\,$\degr$.
 There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained due to the slower cooling of larger grains (cite Casassus?).
@@
 \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner ring.
-Accordingly, taking the parametric model values for the large-dust inner ring we can have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 4\,M$_{\earth}$.
+Accordingly, taking the parametric model values for the large-dust inner ring we can have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
 
@@
 
+%\begin{table}
+% \caption{Model rings masses}
+% \label{tab:masses}
+% \begin{tabular}{lcc}
+%  \hline
+%  Ring & Location & Mass\\
+%   & $\mathrm{au}$ & $M_{\earth}$ \\
+%  \hline
+%  First & 5 to 8 & 0.0007 \\
+%  Second & 11 to 19 & 2.9 \\
+%  Third & 20 to 80 & 43 \\
+%  \hline
+% \end{tabular}
+%\end{table}
+
 \section{Conclusions} \label{sec:Conclusions}
@@
   \item We report a narrow inner ring for the 1.3\,mm continuum at $r$ = 13.46$\pm$0.43\,au and has an estimated width of 4.17$\pm$0.94\,au.
-The location of this ring is similar to the inner ring observed in the scattered light image, this reveals that the ring includes a considerable mass of millimetre-sized grains of around 4\,M$_{\earth}$.
+The location of this ring is similar to the inner ring observed in the scattered light image, this reveals that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
 Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.

### 2020-10-02 mnras_template.tex
Add files via upload

@@
     V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that has a gas-rich circumbinary disc.
-    We report on new $\sim20$\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
+    We report on new $\sim$20\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
 We use a parametric a radiative transfer model of the circumbinary disc, computed with \textsc{radmc3d} to interpret the available data, including the spectral-energy-distribution, in terms of a physical model.
 In addition, we explore decompositions of the imaging data in polar coordinates to better constrain the disc radial structure.
-    We report a two ringed structure for the millimetre-size dust population with a narrow, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au. 
+    We report a two ringed structure for the millimetre-size dust population with a narrow, less than 4.17$\pm$0.94\,au-wide inner ring located at 13.46$\pm$0.43\,au. 
     This ring is the finest reported so far in a gas rich protoplanetary disc. 
-    The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au. The radial profile of the outer ring exhibits an intriguing break at $\sim$35\,au. 
-    %The RT model reproduces accurately the available data.
+    The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au. 
+    %The radial profile of the outer ring exhibits an intriguing break at $\sim$35\,au. 
+    The RT model reproduces accurately the available data.
     %We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations. 
@@
 This report is part of a survey of discs around T-Tauri Stars (DARTSS - ref Avenhaus, Perez et al in pret).
-Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr, which is a remarkable system where we can observe fundamental processes associated with disc evolution.
+Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr, which is a remarkable system where it is possible to observe fundamental processes associated with disc evolution.
 
@@
 We can then calculate the binary phase at the time of the ALMA observation at $\phi=$13\,$\degr$.
-There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained due to the slower cooling of larger grains (cite Casassus?).
+There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained due to the slower cooling of larger grains (cite Casassus?***).
 
@@
 The model reproduced the two rings that are present in the observation: the faint inner ring and the outer brighter one.
-The outer ring has an intensity peak at $\sim$30\,au and a break present at $\sim$35\,au.
-
+%The outer ring has an intensity peak at $\sim$30\,au and a break present at $\sim$35\,au.
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.
@@
 \begin{itemize}
-  \item We report a narrow inner ring for the 1.3\,mm continuum at $r$ = 13.46$\pm$0.43\,au and has an estimated width of 4.17$\pm$0.94\,au.
+  \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au.
 The location of this ring is similar to the inner ring observed in the scattered light image, this reveals that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.

### 2020-10-02 mnras_template.tex
Add files via upload

@@
 To analyse the new ALMA data, we aim to reproduce the disc through a parametric model ran with the radiative transfer code \textsc{radmc3d} \citep{Dullemond_2012} so that the model would agree with the ALMA observation, a previous SPHERE-IRDIS observation and the Spectral Energy Distribution (SED).
-With the model representation of the dust density distribution and combined with a decomposition in polar coordinates of the ALMA image we can have better approximations of the radial structure of the disc.
+Combining the model representation of the dust density distribution with a decomposition in polar coordinates of the ALMA image we can have better approximations of the radial structure of the disc.
 It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grains disc.
 
-In the following sections, first we describe the new 1.3\,mm continuum observation alongside with a SPHERE-IRDIS \textit{H}-band image (Section \ref{sec:Observations}), present the structure of the parametric model used to simulate the disc (Section \ref{sec:model}), comment on the results of the comparison of the model with the data and a discussion of the main results (Section \ref{sec:results}).
-Finally, we share our main conclusions in Section \ref{sec:Conclusions}.
+The structure of this letter is as follows.
+The new 1.3\,mm continuum observation is described alongside with a SPHERE-IRDIS \textit{H}-band image in Section \ref{sec:Observations}.
+The structure of the parametric model used to simulate the disc is presented in Section \ref{sec:model}.
+The results of the model and the discussion are commented Section \ref{sec:results} and the main conclusions are described in Section \ref{sec:Conclusions}.
 
@@
 These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered light accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
-By comparing both we can determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+By comparing both is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
 
@@
 The survey simultaneously mapped 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-In this work we focus exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs05$.
+This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs05$.
 
-For this investigation we made use of previous polarimetric image (at 1.65$\micron$) taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument.
-A complete description of these image and all about data reduction was reported in \citet{Avenhaus_2018}.
+In this investigation, a previous polarimetric image at 1.65\,$\micron$ is used.
+The image was taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument, a complete description of the image and all about data reduction was reported in \citet{Avenhaus_2018}.
 
-For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the \textsc{uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} we can super-resolve the clean beam, obtaining an effective angular resolution $\sim$2-3 times higher than in the clean image with natural weights.
+For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the \textsc{uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$2-3 times higher than in the clean image with natural weights.
 The model obtains this higher resolution through fitting the data using Chi-squared minimisation.
@@
 The outer ring has its peak intensity at $\sim$30\,au and reaches out to $\sim$60\,au.
-Additionally, we can observe that there is a surface brightness break at $\sim$35\,au, another feature that has never been considered.
+Additionally, there is a surface brightness break at $\sim$35\,au, another feature that has never been considered.
 
@@
 \ref{fig:polarring}).
-As we are using the \textsc{uvmem} model image and the effective angular resolution is $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs05$), these measurements only gives as an upper limit of the real width.
+As the \textsc{uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs05$), these measurements only gives an upper limit of the real width.
 
@@
 \citet{dOrazi} also measured the binary phase in the scattered light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
-We can then calculate the binary phase at the time of the ALMA observation at $\phi=$13\,$\degr$.
+Using this measurement, the binary phase was calculated at the time of the ALMA observation at $\phi=$13\,$\degr$.
 There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained due to the slower cooling of larger grains (cite Casassus?***).
@@
 Given the observations, we consider that a correct approach for this disc is using two different dust populations: larger grains that are vertically settled and dominates the disc mass and a less-abundant population of smaller grains that are distributed to larger heights from the mid-plane.
-As the gas and the small-dust population are coupled, it is important to consider the gas in the modelling process, but we are not predicting line emissions.
+As the gas and the small-dust population are coupled, it is important to consider the gas in the modelling process, but no line emission prediction is made.
 
@@
 \end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used a fixed $\gamma$ = 1, a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
 
@@
 Since the large-dust grains are less coupled to the gas, their distribution has some important differences.
-We leave a large inner cavity and added another scaling factor (or filter) to generate the larger gap between the rings.
-For the inner ring we use the same profile as the gas but with different values for $R_c$ and $\Sigma_c$.
+A large inner cavity and another scaling factor (or filter) to generate the larger gap between the rings are needed.
+For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$.
 The greatest difference is in the outer ring, where we used a sum of an exponential correction with a Gaussian function and, between 32 and 34.5\,au, in an effort to recreate the break seen in the profile, we chose a different value for $\gamma$ = -8.
-Then we have
+So, for the large dust grains, the surface density is
 
@@
 
-Also for both dust populations, the inner part of the outer ring follows a different behaviour. To model that parts we multiplied by an additional factor $\epsilon(r)$
+Also for both dust populations, the inner part of the outer ring follows a different behaviour. The surface density profile is multiplied by an additional factor
 \begin{equation}
@@
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-For that matter, we used two different flaring index $\psi$ for our model.
+For that matter, the model uses two different flaring index $\psi$.
 The separation between the two values was set at $r$ = 19\,au with values of 0.2 and 0.5 for the inner part and the outer part respectively.
@@
 = 74.6\,$\degr$.
-Finally, we set the distance at d = 72.4\,pc \citep{Gaia}.
+Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.
 
@@
 \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner ring.
-Accordingly, taking the parametric model values for the large-dust inner ring we can have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
+Accordingly, taking the parametric model values for the large-dust inner ring we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
 

### 2020-10-06 mnras_template.tex
Add files via upload

@@
 \begin{abstract}
-   %%%%context
+    %context
     V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that has a gas-rich circumbinary disc.
-    We report on new $\sim$20\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
+    %aim
+    We report on new $\sim20$\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
+    %methods
     We use a parametric a radiative transfer model of the circumbinary disc, computed with \textsc{radmc3d} to interpret the available data, including the spectral-energy-distribution, in terms of a physical model.
 In addition, we explore decompositions of the imaging data in polar coordinates to better constrain the disc radial structure.
-    We report a two ringed structure for the millimetre-size dust population with a narrow, less than 4.17$\pm$0.94\,au-wide inner ring located at 13.46$\pm$0.43\,au. 
+    %results
+    We report a two ringed structure for the millimetre-size dust population with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au.
 This ring is the finest reported so far in a gas rich protoplanetary disc.
 The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au.
-    %The radial profile of the outer ring exhibits an intriguing break at $\sim$35\,au. 
+The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au.
 The RT model reproduces accurately the available data.
-    %We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations. 
-    %The shadow of the secondary reported previously from the scattered-light data is also reproduced by the RT model. 
-    %The DPI image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with rather large dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains. 
+We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations.
+The shadow of the secondary reported previously from the scattered-light data is also reproduced by the RT model.
+    %conclusions
+    The DPI image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with rather large dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains.
 Using the parametric model scale height as an estimated height, we found that the thin inner ring is stable.
-    %Deeper ALMA observations may confirm the lopsided 5\,au ring.
+Deeper ALMA observations may confirm the lopsided 5\,au ring.
 
@@
 This report is part of a survey of discs around T-Tauri Stars (DARTSS - ref Avenhaus, Perez et al in pret).
-Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr, which is a remarkable system where it is possible to observe fundamental processes associated with disc evolution.
+Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr.
 
@@
 
-To analyse the new ALMA data, we aim to reproduce the disc through a parametric model ran with the radiative transfer code \textsc{radmc3d} \citep{Dullemond_2012} so that the model would agree with the ALMA observation, a previous SPHERE-IRDIS observation and the Spectral Energy Distribution (SED).
+To analyse the new ALMA data, the aim was to reproduce the disc through a parametric model computed with the radiative transfer code \textsc{radmc3d} \citep{Dullemond_2012} and thus be able to interpret the data in terms of a physical model.
+The model would have to agree not only with the new ALMA observation but also with a previous SPHERE-IRDIS observation and the Spectral Energy Distribution (SED).
 Combining the model representation of the dust density distribution with a decomposition in polar coordinates of the ALMA image we can have better approximations of the radial structure of the disc.
-It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grains disc.
+It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grain disc.
 
@@
 These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered light accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
-By comparing both is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
 
@@
 
-In this investigation, a previous polarimetric image at 1.65\,$\micron$ is used.
+In this investigation a previous polarimetric image at 1.65\,$\micron$ is used.
 The image was taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument, a complete description of the image and all about data reduction was reported in \citet{Avenhaus_2018}.
@@
 \ref{fig:two} exhibits previously unseen substructure of the disc.
-This unique high-definition image reveals that the disc features a two-ring structure for the large grain dust with a broad gap between the rings.
-The wide and brighter outer ring has been observed in previous occasions, but the thin and weak inner ring has never seen before (\citet{Ru_z_Rodr_guez_2019} anticipated its existence).
-The outer ring has its peak intensity at $\sim$30\,au and reaches out to $\sim$60\,au.
-Additionally, there is a surface brightness break at $\sim$35\,au, another feature that has never been considered.
+This image reveals that the disc features two rings of large dust grains with a broad gap between them.
+The wide and brighter outer ring has its peak intensity at $\sim$30\,au, has a surface brightness break at $\sim$35\,au, and reaches out to $\sim$60\,au.
+The thin and weak inner ring had never seen before, but \citet{Ru_z_Rodr_guez_2019} did anticipate its existence.
 
@@
 
-The inner ring is surprisingly narrow, and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig.
+The inner ring is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig.
 \ref{fig:two}).
-The ring width can be measured in polar coordinates, following the determination of the inner ring centre and orientation.
+The ring width can be measured in polar coordinates following the determination of the inner ring centre and orientation.
 We minimised the dispersion of the disc radial profiles, from 6\,au to 19\,au (aiming for the inner ring) for a PA of 74.6\,$\degr$, an inclination of 33.9\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.
 
-Assuming a Gaussian dust inner ring, we obtained the mean width and the location of the ring by finding for each azimuth the Gaussian intensity profile that best describes the ring.
+Assuming a Gaussian dust inner ring, we obtained its mean width and location by finding for each azimuth the Gaussian intensity profile that best describes the ring.
 This gave us a FWHM of 4.17$\pm$0.94\,au and that it is located at 13.46$\pm$0.43\,au from the stars (See Fig.
@@
 Doing one more time the minimisation of the dispersion of the disc radial profiles, but this time aiming for the outer ring from 20\,au to 70\,au, for a PA of 76.8\,$\degr$, with an inclination of 34.0\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars, we can compare the measured location of the inner ring according with this parameters versus to the location obtained before.
-The deviation is shown in Fig.
-\ref{fig:polarring} and is not trivial since it depend on a few parameters such as the different inclinations of the rings, the difference in position angle and the small shifts of the centres relative to the stars.
-Those parameters play an important role, but a possible small difference in eccentricities between the inner and the outer ring could also help explain this deviation between the two measurements.
+The deviation for each azimuth is shown in Fig.
+\ref{fig:polarring}, and is not trivial since it depend on a few parameters such as the different inclinations of the rings, the difference in position angle and the shift of the centres relative to the stars.
+But even though those parameters play an important role, a possible small difference in eccentricities between the inner and the outer ring could also help explain this deviation between the two measurements.
 ***
@@
 
-Our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model
-are shown in Fig. \ref{fig:two} and Fig. \ref{fig:SED} respectively.
+Our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model are shown in Fig. \ref{fig:two} and Fig. \ref{fig:SED} respectively.
 
-The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations displaying a two ringed disc, where the innermost small-dust ring of the parametric model hides under the artificial coronagraph.
+The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where the innermost small-dust ring of the parametric model hides under the artificial coronagraph.
 The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains.
@@
 The model reproduced the two rings that are present in the observation: the faint inner ring and the outer brighter one.
-%The outer ring has an intensity peak at $\sim$30\,au and a break present at $\sim$35\,au.
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.
@@
 Accordingly, taking the parametric model values for the large-dust inner ring we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
+For the outer ring, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$
 
@@
 For a ring to be stable and long-lived its horizontal dimension can not be less than its vertical height.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of the inner ring (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable and the disc is capable of supporting a thin ring as this one.
+Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of the inner ring (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable.
 
@@
 New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr reveals new information about its substructure.
-Using a radiative transfer model, a preexisting scattered light observation and decompositions in polar coordinates of the computed \textsc{uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
+Using a radiative transfer model and decompositions in polar coordinates of the computed \textsc{uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
 
@@
   \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au.
-The location of this ring is similar to the inner ring observed in the scattered light image, this reveals that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
+The location of this ring is similar to the inner ring observed in the scattered light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
 Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.
@@
 
-  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
+  \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
 

### 2020-10-06 mnras_template.tex
Add files via upload

@@
 
-For the representation of the stars we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with  T$_{\mathrm{eff},1}=$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2}=$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}}= -$9.3$\pm$0.3\,Myr$^{-1}$ for both cases.
-The stars were placed with a separation of 0.041\,au and arranged with a 30\,$\degr$ rotation to mach the shadows reported by \citet{dOrazi}.
+For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
+The stars were placed with a separation of 0.041\,au and oriented with a 30\,$\degr$ rotation, relative to the semi-major axis of the disk, to mach the shadows reported by \citet{dOrazi}.
 
@@
 We choose to build the model by thinking the components of the disc separately and then unite them as a whole.
-Given the observations, we consider that a correct approach for this disc is using two different dust populations: larger grains that are vertically settled and dominates the disc mass and a less-abundant population of smaller grains that are distributed to larger heights from the mid-plane.
+Given the observations that we are using, we consider that a correct approach for this disc is using two different dust populations: larger grains that are vertically settled and dominates the disc mass and a less-abundant population of smaller grains that are distributed to larger heights from the mid-plane.
 As the gas and the small-dust population are coupled, it is important to consider the gas in the modelling process, but no line emission prediction is made.

### 2020-10-06 mnras_template.tex
Update mnras_template.tex
Add files via upload

@@
 
-Assuming a three dimensional model in a spherical reference frame with coordinates (r, $\theta$, $\phi$), gas density ($\rho_{\mathrm{gas}}$) distribution follows
+Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $\phi$), gas density ($\rho_{\mathrm{gas}}$) distribution follows
 \begin{equation}
-  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \text{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right].
+  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right].
 \end{equation}
@@
 \begin{equation}
-  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \text{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
+  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
 \end{equation}
@@
 
-The small-dust density distribution follows the same behaviour as the gas but with different scaling factors: the dust-to-gas ratio ($\zeta$ = 0.047 as \citet{Rosenfeld_2013}), the mass fraction between small and large dust particles ($f_{\mathrm{mass}}$) and a $\delta(r)$ factor for fine tuning that depends on the radius.
+The small-dust density distribution follows the same behaviour as the gas but with different scaling factors: the dust-to-gas ratio ($\zeta$ = 0.047 as \citet{Rosenfeld_2013}), the mass fraction between small and large dust particles ($f_{\mathrm{mass}}$) and another $\delta_{\mathrm{sd}}(r)$ factor for fine tuning that depends on the radius.
 So it is
 \begin{equation}
-\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{mass}} \, \delta(r) \: \zeta .
+\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{mass}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
 \end{equation}
@@
 Since the large-dust grains are less coupled to the gas, their distribution has some important differences.
-A large inner cavity and another scaling factor (or filter) to generate the larger gap between the rings are needed.
+A large inner cavity and another scaling factor (or filter) is needed to generate the larger gap between the rings.
 For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$.
@@
 \begin{multline}
-  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \text{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \text{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
+  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
 \end{multline}
@@
     \caption{The SED (black points and solid red curve) compared with the model (blue).
-The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.}
+The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
+The dashed silver curve shows the emission of the stellar photosphere model.}
     \label{fig:SED}

### 2020-10-08 Draft_V4046Sgr_mnras.tex
Rename Draft_mnras.tex to Draft_V4046Sgr_mnras.tex

--- 2020-10-06 mnras_template.tex
@@
     %aim
-    We report on new $\sim20$\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
+    We report on new $\sim$20\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
     %methods
@@
 
-Disc structures can be explored by means of comparing mm continuum and scattered light images.
-These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered light accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
-By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+Disc structures can be explored by means of comparing mm continuum and scattered-light images.
+These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
+By comparing both, is easier to determine whether asymmetries in scattered-light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
 
@@
 The wide and brighter outer ring has its peak intensity at $\sim$30\,au, has a surface brightness break at $\sim$35\,au, and reaches out to $\sim$60\,au.
-The thin and weak inner ring had never seen before, but \citet{Ru_z_Rodr_guez_2019} did anticipate its existence.
+The thin and weak inner ring had never seen before, however \citet{Ru_z_Rodr_guez_2019} did anticipate its existence.
 
@@
 
-The scattered light image shown in Fig.
+The scattered-light image shown in Fig.
 \ref{fig:two} reveals the presence of a double ring structure in the micron-sized dust distribution.
@@
 
-\citet{dOrazi} also measured the binary phase in the scattered light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
+\citet{dOrazi} also measured the binary phase in the scattered-light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at $\phi=$13\,$\degr$.
@@
   \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au.
-The location of this ring is similar to the inner ring observed in the scattered light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
+The location of this ring is similar to the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
 Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.
@@
   \item As our parametric model accounts for the SED of the system, the disc requires the existence of a sub-micron dust population close (<5\,au) to the stars.
-We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains that lies under the coronagraph of the SPHERE images.
+We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains that lies under the coronagraph of the scattered-light image.
 Additionally, the weak central emission at 1.3\,mm could be part of this ring.

### 2020-10-08 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 
-\title[V4046\,Sgr high-resolution ALMA observations]{V4046\,Sgr high-resolution 1.3\,mm continuum ALMA observations: a disc with a thin ring}
+\title[High-resolution ALMA observations of V4046\,Sgr]{High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring}
 
@@
 These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
-By comparing both, is easier to determine whether asymmetries in scattered-light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
+By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.
 

### 2020-10-09 Draft_V4046Sgr_mnras.tex
Add files via upload

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[letters, usenatbib]{mnras}
+\documentclass[letters,usenatbib,times]{mnras}
 
@@
 \usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
+%% \usepackage{amsmath}	% Advanced maths commands
+%% \usepackage{amssymb}	% Extra maths symbols
 
@@
 \begin{abstract}
-    %context
-    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that has a gas-rich circumbinary disc.
-    %aim
-    We report on new $\sim$20\,mas resolution Atacama Large Millimeter Array (ALMA) observations of the radio continuum at 1.3\,mm, and compare with archival SPHERE-IRDIS differential polarised imaging (DPI) of scattered-light at H-band (1.65\,$\micron$) to reach conclusions on the disc structure.
-    %methods
-    We use a parametric a radiative transfer model of the circumbinary disc, computed with \textsc{radmc3d} to interpret the available data, including the spectral-energy-distribution, in terms of a physical model.
-In addition, we explore decompositions of the imaging data in polar coordinates to better constrain the disc radial structure.
-    %results
-    We report a two ringed structure for the millimetre-size dust population with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au.
-This ring is the finest reported so far in a gas rich protoplanetary disc.
+    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that hosts a gas-rich disc known for its wide gaps and dusty ring as seen by the Atacama Large Millimeter/submillimeter Array (ALMA).
+We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm radio continuum.
+These observations, combined with SPHERE-IRDIS polarized scattered light images, allow us to characterize the disc structure.
+We reproduce the available observations, including the spectral energy distribution, in terms of a physical structure using a parametric radiative transfer (RT) model.
+We report a two-ringed structure for the 1.3 mm dust emission with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au.
 The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au.
+We deproject the images in polar coordinates to better constrain the disc radial structure.
 The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au.
-The RT model reproduces accurately the available data.
-We predict a three ringed structure for the small-dust population with a inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations.
-The shadow of the secondary reported previously from the scattered-light data is also reproduced by the RT model.
-    %conclusions
-    The DPI image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with rather large dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains.
-Using the parametric model scale height as an estimated height, we found that the thin inner ring is stable.
-Deeper ALMA observations may confirm the lopsided 5\,au ring.
-
-%briefly describe the aims, methods, and main results
-%single paragraph not more than 250 words
-%No references should appear
+The model predicts a three-ringed structure for the small-dust population with an inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations.
+The shadow of the secondary star reported previously from scattered-light data is also reproduced by our RT model.
+The polarized light image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains.
+Using the parametric model scale-height as an estimated height, we found that the thin inner ring is stable.
+Deeper ALMA observations may confirm the lopsided 6\,au ring.
 \end{abstract}
@@
 
-Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
-This report is part of a survey of discs around T-Tauri Stars (DARTSS - ref Avenhaus, Perez et al in pret).
+Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
+***EXPAND, I would give a general description on substructures and cite ``e.g.
+Andrews (2020) for a recent review''***
+
+V4046 Sagittarii (Sgr) is is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+The V4046\,Sgr system, located at 72.41$\pm$0.34\,pc \citep{Gaia}, is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}.
+The V4046\,Sgr binary system hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}.
+The disc has a vast variety of molecules with a detailed sub-arcsecond ALMA molecular line imaging study by \citet{Kastner_2018}.
+
+The Disks ARound T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE).
+The sample is not biased towards exceptionally bright and large disks, and consists of only solar-mass stars.
+A second part of the survey increased the number of sources by presenting 21 new images of circumstellar disks \citep{Garufi2020}.
+The observations revealed diversed structures and morphologies in the scattering surface of these disks.
+This letter is part of our new DARTTS survey with ALMA (DARTTS-A) which will present millimeter observations of nine protoplanetary disks previously imaged in polarized scattered light in DARTTS-S.
+
 Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr.
-
-V4046 Sagittarii (Sgr) is is a double-lined spectroscopic binary of a nearly equal-mass pair of K-type stars (K5 and K7) with masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}.
-The V4046\,Sgr system locate at 72.41$\pm$0.34\,pc \citep{Gaia}, and is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, fixing its age at 23$\pm$3\,Myr \citep{Mamajek_2014}.
-V4046\,Sgr binary system is surrounded by a massive ($\sim$0.1\,M$_{\sun}$), gas-rich disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}.
-The disc has a vast variety of molecules with a detailed subarcsecond ALMA molecular line imaging study by \citet{Kastner_2018}.
-The chemical structure is composed of CO and HCN that display centrally peaked morphologies, a sequence of sharp and diffuse rings of complex nitrile group molecules (HC$_3$N, CH$_3$CN), deuterated molecules (DCN, DCO$^+$), hydrocarbons (C$_2$H) and others like N$_2$H$^+$, H$_2$CO.
-
-To analyse the new ALMA data, the aim was to reproduce the disc through a parametric model computed with the radiative transfer code \textsc{radmc3d} \citep{Dullemond_2012} and thus be able to interpret the data in terms of a physical model.
-The model would have to agree not only with the new ALMA observation but also with a previous SPHERE-IRDIS observation and the Spectral Energy Distribution (SED).
-Combining the model representation of the dust density distribution with a decomposition in polar coordinates of the ALMA image we can have better approximations of the radial structure of the disc.
-It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grain disc.
-
 The structure of this letter is as follows.
@@
 The structure of the parametric model used to simulate the disc is presented in Section \ref{sec:model}.
+It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grain disc.
 The results of the model and the discussion are commented Section \ref{sec:results} and the main conclusions are described in Section \ref{sec:Conclusions}.
@@
 
-Disc structures can be explored by means of comparing mm continuum and scattered-light images.
+%% Disc structures can be explored by means of comparing mm continuum and scattered-light images.
 These observations allow us to see the distribution of different populations of dust particles, while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off small micron-sized dust at the disc surface layer, high above the mid-plane.
@@
 
-New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S..
-These were taken in the context of a larger survey for 14 optically visible TTauri discs at $\sim$50\,mas resolution.
+New ALMA observations of V4046\,Sgr were obtained in 2017 as part of the Cycle 5 program 2017.1.01167.S (PI: S.
+Perez).
+These were acquired in the context of a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution, the DARTTS-A program (Perez et al.
+{\em in prep}).
 The survey simultaneously mapped 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs05$.
+This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs05$ (in natural weights).
 
-In this investigation a previous polarimetric image at 1.65\,$\micron$ is used.
-The image was taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument, a complete description of the image and all about data reduction was reported in \citet{Avenhaus_2018}.
+In this investigation, we use the previous polarimetric image at 1.65\,$\micron$ part of the DARTTS-SPHERE I survey \citep{Avenhaus_2018}.
+The image was taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument in differential polarization imaging (DPI) mode, and a complete description of the data reduction was presented in \citet{Avenhaus_2018}.
 
@@
 The model obtains this higher resolution through fitting the data using Chi-squared minimisation.
-Here we adopted a pure $\chi ^2$ model image.
+Here we adopted a pure $\chi^2$ model image.
 The resulting \textsc{uvmem} image shown in Fig.
@@
 For all the images in the figure the colour scale is linear.}
-
   \label{fig:two}
@@
 
-Interestingly, the ALMA images also detects faint the 1.3\,mm continuum near the stellar positions (See the inset in Fig.
+Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.
 \ref{fig:two}).
@@
 For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
-The stars were placed with a separation of 0.041\,au and oriented with a 30\,$\degr$ rotation, relative to the semi-major axis of the disk, to mach the shadows reported by \citet{dOrazi}.
+The stars were placed with a separation of 0.041\,au and oriented with a 30\,$\degr$ rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi}.
 
@@
 
-Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $\phi$), gas density ($\rho_{\mathrm{gas}}$) distribution follows
+Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $\phi$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
 \begin{equation}
@@
 
-We define the parametric scale height profiles for the gas and for each dust population as \begin{equation}
+We define the parametric scale height profiles for the gas and for each dust population as
+\begin{equation}
     \label{scale}
@@
 The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains.
-Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the Sphere-IRDIS image.
+Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
 
@@
 The key conclusions of our analysis are as follows.
-\begin{itemize}
+\begin{enumerate}
+
   \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au.
@@
 Additionally, the weak central emission at 1.3\,mm could be part of this ring.
-
-\end{itemize}
+\end{enumerate}
 

### 2020-10-09 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 \begin{abstract}
-    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that hosts a gas-rich disc known for its wide gaps and dusty ring as seen by the Atacama Large Millimeter/submillimeter Array (ALMA).
+    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that hosts a gas-rich disc known for its wide gaps and dusty ring as seen by the Atacama Large Millimeter/submillimetre Array (ALMA).
 We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm radio continuum.
@@
 
-Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
+Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
 ***EXPAND, I would give a general description on substructures and cite ``e.g.

### 2020-10-10 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 The survey simultaneously mapped 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs05$ (in natural weights).
+This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs06$ (in natural weights).
 
@@
 Top right panel: 1.3\,mm continuum \textsc{uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs05$.
+The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs06$.
 The inset displays a enlarged view of the central emission, the green star marks the star positions.
@@
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The yellow ellipse shows the size of the simulated beam: $ 0\farcs04 \, \times \, 0\farcs05$.
+The yellow ellipse shows the size of the simulated beam: $ 0\farcs04 \, \times \, 0\farcs06$.
 For all the images in the figure the colour scale is linear.}
@@
 \ref{fig:polarring}).
-As the \textsc{uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs05$), these measurements only gives an upper limit of the real width.
+As the \textsc{uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), these measurements only gives an upper limit of the real width.
 

### 2020-10-13 Draft_V4046Sgr_mnras.tex
with SC edits

@@
 \author[R. Martinez Brunner et al.]{
-R. Martinez-Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
-A. N. Other,$^{2}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
+Rafael Martinez-Brunner,$^{1}$\thanks{E-mail: rmartinezbrunner@gmail.com}
+Simon Casassus,$^{1}$
+Sebasti\'an P\'erez,$^{2}$
+et al. 
 \\
 % List of institutions
-$^{1}$Chile\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
+$^{1}$Departamento de Astronom\'{\i}a, Universidad de Chile, Casilla 36-D, Santiago, Chile\\
+$^{2}$Universidad de Santiago de Chile, Av. Ecuador 3659, Santiago\\
 }
@@
 \begin{abstract}
-    V4046 Sgr is a nearby pre-main sequence spectroscopic binary system that hosts a gas-rich disc known for its wide gaps and dusty ring as seen by the Atacama Large Millimeter/submillimetre Array (ALMA).
-We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm radio continuum.
-These observations, combined with SPHERE-IRDIS polarized scattered light images, allow us to characterize the disc structure.
-We reproduce the available observations, including the spectral energy distribution, in terms of a physical structure using a parametric radiative transfer (RT) model.
-We report a two-ringed structure for the 1.3 mm dust emission with a narrow, previously unseen, less than 4.17$\pm$0.94\,au-wide inner ring centred at 13.46$\pm$0.43\,au.
-The ring is surrounded by a $\sim$9\,au-wide gap, flanked by a very sharp outer ring starting at 24\,au.
-We deproject the images in polar coordinates to better constrain the disc radial structure.
-The radial profile of the outer ring exhibits an intriguing discontinuity at $\sim$35\,au.
-The model predicts a three-ringed structure for the small-dust population with an inner ring at $\sim$6\,au hiding under the coronagraph in the SPHERE observations.
-The shadow of the secondary star reported previously from scattered-light data is also reproduced by our RT model.
-The polarized light image reveals strong forward-scattering at 1.65\,$\micron$, which we reproduced with dust grains of no less than 0.4\,$\micron$, hinting at a deficit of very-small-grains.
-Using the parametric model scale-height as an estimated height, we found that the thin inner ring is stable.
-Deeper ALMA observations may confirm the lopsided 6\,au ring.
+  The nearby V4046\,Sgr spectroscopic binary  hosts a gas-rich disc known for its wide cavity and dusty ring.
+We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm  continuum.
+The comparison of these  observations, combined with SPHERE-IRDIS polarized  images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the RADMC3D package, allow us to propose a physical model for the source.
+The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of  4.17$\pm$0.94\,au.
+Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap , and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
+The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail.
+The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disk.
+Faint mm-continuum coincident with Ring6 is picked up by ALMA, whose morphology  suggests that Ring6  is lopsided or shadowed by the secondary.
+The previously reported scattered-light shadow of the secondary star is  also reproduced by the RT model.
+The surpising  thin Ring13 is nonetheless **10*** times wider than the model scale height, and could thus be long-lived.
+The strong near-far disc asymmetry  at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires  grain radii  of no less than  0.4\,$\micron$.
 \end{abstract}
@@
 
-Recent observations of circumstellar discs have revolutionised the way we think about protoplanetary discs, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has been mainly been towards the brighter sources.
-***EXPAND, I would give a general description on substructures and cite ``e.g.
-Andrews (2020) for a recent review''***
-
-V4046 Sagittarii (Sgr) is is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}.
-The V4046\,Sgr system, located at 72.41$\pm$0.34\,pc \citep{Gaia}, is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}.
-The V4046\,Sgr binary system hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}.
-The disc has a vast variety of molecules with a detailed sub-arcsecond ALMA molecular line imaging study by \citet{Kastner_2018}.
-
+Recent observations of young circumstellar discs have transformed  current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has  mainly been towards the brighter sources \citep[see][for a review]{Andrews2020arXiv200105007A}.
 The Disks ARound T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE).
@@
 The observations revealed diversed structures and morphologies in the scattering surface of these disks.
-This letter is part of our new DARTTS survey with ALMA (DARTTS-A) which will present millimeter observations of nine protoplanetary disks previously imaged in polarized scattered light in DARTTS-S.
+This letter on V4046 Sagittarii (Sgr) is part of our new DARTTS survey with ALMA (DARTTS-A) which will present millimeter observations of nine protoplanetary disks previously imaged in polarized scattered light in DARTTS-S.
 
-Here, we present new 1.3\,mm continuum ALMA observation of V4046\,Sgr.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is  72.41$\pm$0.34\,pc \citep{Gaia}.
+V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical  diversity  \citep{Kastner_2018}.
+
 The structure of this letter is as follows.
-The new 1.3\,mm continuum observation is described alongside with a SPHERE-IRDIS \textit{H}-band image in Section \ref{sec:Observations}.
-The structure of the parametric model used to simulate the disc is presented in Section \ref{sec:model}.
-It is worth mentioning that previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but with the difference that our new reference observation of radio wavelengths has a sub-arcsecond resolution, allowing us to discover previously unseen underlying substructures of the large-dust grain disc.
-The results of the model and the discussion are commented Section \ref{sec:results} and the main conclusions are described in Section \ref{sec:Conclusions}.
+The observations, including  new 1.3\,mm continuum data, are described in Section \ref{sec:Observations}.
+We interpret the data in terms of a parametric model,  presented in Section \ref{sec:model}.
+Previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but our new ALMA data bring additional information.
+Our results are discussed in  Section \ref{sec:results} and summarised in  Section \ref{sec:Conclusions}.
 
@@
 Perez).
-These were acquired in the context of a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution, the DARTTS-A program (Perez et al.
-{\em in prep}).
-The survey simultaneously mapped 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
+These were acquired in the context of the DARTTS-A program (Perez et al.
+{\em in prep}), a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution.
+The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
 This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs06$ (in natural weights).
+**Seba, sure that the survey only used C43-8?***
 
-In this investigation, we use the previous polarimetric image at 1.65\,$\micron$ part of the DARTTS-SPHERE I survey \citep{Avenhaus_2018}.
+In this investigation, we use the  polarimetric image at 1.65\,$\micron$ previously published as part of the DARTTS-SPHERE I survey \citep{Avenhaus_2018}.
 The image was taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument in differential polarization imaging (DPI) mode, and a complete description of the data reduction was presented in \citet{Avenhaus_2018}.
 
-For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the \textsc{uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$2-3 times higher than in the clean image with natural weights.
-The model obtains this higher resolution through fitting the data using Chi-squared minimisation.
-Here we adopted a pure $\chi^2$ model image.
+For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the \textsc{uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than  natural weights.
+The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
+Here we adopted a pure $\chi^2$ model image ***sure about this?
+what is the name of the image you used?****.
 The resulting \textsc{uvmem} image shown in Fig.
 \ref{fig:two} exhibits previously unseen substructure of the disc.
-This image reveals that the disc features two rings of large dust grains with a broad gap between them.
-The wide and brighter outer ring has its peak intensity at $\sim$30\,au, has a surface brightness break at $\sim$35\,au, and reaches out to $\sim$60\,au.
-The thin and weak inner ring had never seen before, however \citet{Ru_z_Rodr_guez_2019} did anticipate its existence.
+This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
+Ring13  at 13\,au and Ring24 starting at 24\,au.
+The wide and bright  Ring24  reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at  $\sim$35\,au into a  shallow tail.
+While this is the first observation of Ring13,  \citet{Ru_z_Rodr_guez_2019} did anticipate its existence ****HOW?
+EXPAND ON THIS***
 
@@
 The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs06$.
-The inset displays a enlarged view of the central emission, the green star marks the star positions.
+The inset zooms into  the central emission, and the green star marks the star positions.
 Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model.
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The yellow ellipse shows the size of the simulated beam: $ 0\farcs04 \, \times \, 0\farcs06$.
+The yellow ellipse shows the size of the  beam: $ 0\farcs04 \, \times \, 0\farcs06$ ***ESTOY CONFUNDIDO POR ESTE BEAM, HAY QUE REPORTAR  1/3 BMAJxBMIN / BPA, INDICANDO 1/3 SEGUIDO POR LOS VALORES EN PESOS NATURALES, Y PLOTEAR EL RESULTADO *****.
 For all the images in the figure the colour scale is linear.}
@@
 
-The inner ring is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig.
+Ring13 is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig.
 \ref{fig:two}).
-The ring width can be measured in polar coordinates following the determination of the inner ring centre and orientation.
-We minimised the dispersion of the disc radial profiles, from 6\,au to 19\,au (aiming for the inner ring) for a PA of 74.6\,$\degr$, an inclination of 33.9\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.
+We determined the ring's center and orientation by  minimising  the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a  PA of 74.6\,$\degr$ ***ADD ERRORES***, an inclination of 33.9\,$\degr$ **ERRORS**** and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.
 
-Assuming a Gaussian dust inner ring, we obtained its mean width and location by finding for each azimuth the Gaussian intensity profile that best describes the ring.
-This gave us a FWHM of 4.17$\pm$0.94\,au and that it is located at 13.46$\pm$0.43\,au from the stars (See Fig.
+The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus  obtaining a width and centroid at each azimuth.
+On average, we obtained  a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of  13.46$\pm$0.43\,au  (See Fig.
 \ref{fig:polarring}).
-As the \textsc{uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), these measurements only gives an upper limit of the real width.
+As the \textsc{uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$) ***CREO QUE AHORA ENTIENDO, HAY QUE ASEGURARTE QUE ESTOS SON LOS BEAMS - DEBIERA SER BMAJORxBMINOR.
+NO CALZA CON EL ABSTRACT ESO SI***, we see that Ring13 is marginally resolved.
+After subtaction of the approximate {\tt uvmem} resolution, the ring width is $\sim$*****.
+****SUBTRACT UVMEM BEAM IN QUADRATURE.****
 
-Doing one more time the minimisation of the dispersion of the disc radial profiles, but this time aiming for the outer ring from 20\,au to 70\,au, for a PA of 76.8\,$\degr$, with an inclination of 34.0\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars, we can compare the measured location of the inner ring according with this parameters versus to the location obtained before.
+Repeating the optimization of the disk orientation, but  this time aiming for Ring24  with a radiual domain from 20\,au to 70\,au, we obtained a  PA of 76.8\,$\degr$ ***ERROrSS***, with an inclination of 34.0\,$\degr$ **ERRORS* and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
+We see that both Ring13 and Ring24  both share / DO NOT SHARE?
+the same orientation and center, given the errors, and both are offset from the star.
+Even though all orientation parameters for Ring13 and Ring24  are consistent within the errors, there  are however some hints for a different orientation, as summarised in Fig.
+\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
+****CALCULATE THE CHI2 DIFFERNCE BETWEEN THE TWO TRACES?
+SOME FORM OF STATS WOULD BE GOOD****
+
+***I WOULD REMOVE THIS OR IDENTIFY SOMETHING CONCRETE OUT OF IT: We can compare the measured location of the inner ring according to  these parameters versus to the location obtained before.
 The deviation for each azimuth is shown in Fig.
@@
 The scattered-light image shown in Fig.
-\ref{fig:two} reveals the presence of a double ring structure in the micron-sized dust distribution.
-The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01 and 24.62$\pm$0.08\,au with a small gap between them at $\sim$20\,au.
-The observed second ring might correspond to the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
+\ref{fig:two} also shows  a double ring structure in the micron-sized dust distribution.
+The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13,  and 24.62$\pm$0.08\,au, coincident with Ring24,  with a small gap between them at $\sim$20\,au.
+The observed second ring  matches   the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
 Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.
 
-\citet{dOrazi} also measured the binary phase in the scattered-light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
+\citet{dOrazi} reported a  binary phase in the scattered-light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at $\phi=$13\,$\degr$.
-There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained due to the slower cooling of larger grains (cite Casassus?***).
+There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained by innefficient disk cooling compared to the speed of the illumination pattern \citep[][]{Casassus2019MNRAS.486L..58C} ***NO ERA DIFICIL ENCONTRAR ESA REF, PORFA LEER AL MENOS EL ABSTRACT****
 
@@
     \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
-    \caption{(a) Polar decomposition of the 1.3\,mm continuum image showing the centres (solid line) of Gaussian fits and the measured FWHM (blue region between the dotted lines) of the inner thin ring for each azimuthal angle.
-This was obtained centring the \textsc{uvmem} image optimising for the outer ring.
-(b) Shows the measured location of the inner ring, where the orange line represents the centres of the fitted Gaussian profile obtained in the first panel and blue line represents the same but obtained centring the \textsc{uvmem} image optimising for the inner ring.}
+    \caption{(a) Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24.
+We  trace Ring13 using the centroids  (solid line) and width of radial Gaussian fits  (blue region between the dotted lines).
+(b) Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in a), while the  blue line is  obtained for the inner ring orientation.}
     \label{fig:polarring}
@@
 
+***HASTA AQUI LLEGUE*****
 \section{Parametric radiative transfer model} \label{sec:model}

### 2020-10-15 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surpising  thin Ring13 is nonetheless **10*** times wider than the model scale height, and could thus be long-lived.
+The surpising thin Ring13 is nonetheless **15** times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 
-Recent observations of young circumstellar discs have transformed  current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has  mainly been towards the brighter sources \citep[see][for a review]{Andrews2020arXiv200105007A}.
+Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}.
 The Disks ARound T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE).
@@
 The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a pure $\chi^2$ model image ***sure about this?
-what is the name of the image you used?****.
+Here we adopted a pure $\chi^2$ model image.
 The resulting \textsc{uvmem} image shown in Fig.
@@
 The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail.
-While this is the first observation of Ring13,  \citet{Ru_z_Rodr_guez_2019} did anticipate its existence ****HOW?
-EXPAND ON THIS***
+While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between
+$\sim$10 and 17\,au.
 
@@
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The yellow ellipse shows the size of the  beam: $ 0\farcs04 \, \times \, 0\farcs06$ ***ESTOY CONFUNDIDO POR ESTE BEAM, HAY QUE REPORTAR  1/3 BMAJxBMIN / BPA, INDICANDO 1/3 SEGUIDO POR LOS VALORES EN PESOS NATURALES, Y PLOTEAR EL RESULTADO *****.
+The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$ ***ESTOY CONFUNDIDO POR ESTE BEAM, HAY QUE REPORTAR 1/3 BMAJxBMIN / BPA, INDICANDO 1/3 SEGUIDO POR LOS VALORES EN PESOS NATURALES, Y PLOTEAR EL RESULTADO *****.
 For all the images in the figure the colour scale is linear.}
@@
 \ref{fig:two}).
-We determined the ring's center and orientation by  minimising  the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a  PA of 74.6\,$\degr$ ***ADD ERRORES***, an inclination of 33.9\,$\degr$ **ERRORS**** and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.
 
@@
 
-Repeating the optimization of the disk orientation, but  this time aiming for Ring24  with a radiual domain from 20\,au to 70\,au, we obtained a  PA of 76.8\,$\degr$ ***ERROrSS***, with an inclination of 34.0\,$\degr$ **ERRORS* and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
+Repeating the optimization of the disk orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
 We see that both Ring13 and Ring24 both share / DO NOT SHARE?
-the same orientation and center, given the errors, and both are offset from the star.
+the same orientation and centre, given the errors, and both are offset from the star.
 Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.
 \ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
-****CALCULATE THE CHI2 DIFFERNCE BETWEEN THE TWO TRACES?
+****CALCULATE THE CHI2 DIFFERENCE BETWEEN THE TWO TRACES?
 SOME FORM OF STATS WOULD BE GOOD****
@@
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at $\phi=$13\,$\degr$.
-There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained by innefficient disk cooling compared to the speed of the illumination pattern \citep[][]{Casassus2019MNRAS.486L..58C} ***NO ERA DIFICIL ENCONTRAR ESA REF, PORFA LEER AL MENOS EL ABSTRACT****
+There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
 
@@
 For the small dust grains, we propose a three ringed structure.
-The innermost ring of the model is located from 5 to 8\,au ,this ring is not present in the observations but was added for having a better SED fit.
-Then follows the two observed rings: the first goes from 12 to 19.5\,au and, with a 1\,au-wide gap between them, the outer ring goes from 20.5\,au and has its maximum density peak at 25\,au.
+The innermost ring of the model is located from 5 to 8\,au (Ring6),this ring is not present in the observations but was added for having a better SED fit.
+Then follows the two observed rings: the first goes from 12 to 19.5\,au (Ring13) and, with a 1\,au-wide gap between them, the outer ring (Ring24) goes from 20.5\,au and has its maximum density peak at 25\,au.
 The small-dust density then then fades as the radius increases.
 
-On the other hand, in order to reproduce the two ringed observed morphology of the millimetre continuum emission we required a model that has its large-dust grain population distributed with a wide central cavity (r = 12.3\,au), a narrow 2.6\,au-wide inner ring followed by a gap of 8.2\,au that separates both rings and then an outer ring that goes from 23\,au and has it density peak at 27.3\,au.
+On the other hand, in order to reproduce the two ringed observed morphology of the millimetre continuum emission we required a model that has its large-dust grain population distributed with a wide central cavity (r = 12.3\,au), a narrow 2.6\,au-wide inner ring (Ring13) followed by a gap of 8.2\,au that separates both rings and then an outer ring (Ring24) that goes from 23\,au and has it density peak at 27.3\,au.
 This last ring has a break between 32 and 34.5\,au and then reaches out to 57\,au.
@@
 For that matter, the model uses two different flaring index $\psi$.
-The separation between the two values was set at $r$ = 19\,au with values of 0.2 and 0.5 for the inner part and the outer part respectively.
+The separation between the two values was set at $r$ = 19\,au with values of 0.2 for the Ring6 and Ring13 and 0.5 for Ring24.
 Also, the scale height is calculated using $H_o$ = 0.045 and $r_0$ = 19.5\,au.

### 2020-10-15 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 
-For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the \textsc{uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights.
+For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem}package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights.
 The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
 Here we adopted a pure $\chi^2$ model image.
-The resulting \textsc{uvmem} image shown in Fig.
+The resulting {\tt uvmem}image shown in Fig.
 \ref{fig:two} exhibits previously unseen substructure of the disc.
@@
 Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc).
-Top right panel: 1.3\,mm continuum \textsc{uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs06$.
+Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
+The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs06$, and the small orange ellipse shows an estimated {\tt uvmem} beam size of: $\sim0\farcs01 \, \times \, \sim0\farcs02$.
 The inset zooms into the central emission, and the green star marks the star positions.
@@
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$ ***ESTOY CONFUNDIDO POR ESTE BEAM, HAY QUE REPORTAR 1/3 BMAJxBMIN / BPA, INDICANDO 1/3 SEGUIDO POR LOS VALORES EN PESOS NATURALES, Y PLOTEAR EL RESULTADO *****.
+The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$.
 For all the images in the figure the colour scale is linear.}
@@
 \ref{fig:polarring}).
-As the \textsc{uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$) ***CREO QUE AHORA ENTIENDO, HAY QUE ASEGURARTE QUE ESTOS SON LOS BEAMS - DEBIERA SER BMAJORxBMINOR.
-NO CALZA CON EL ABSTRACT ESO SI***, we see that Ring13 is marginally resolved.
-After subtaction of the approximate {\tt uvmem} resolution, the ring width is $\sim$*****.
-****SUBTRACT UVMEM BEAM IN QUADRATURE.****
+As the {\tt uvmem}model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), we see that Ring13 is marginally resolved.
+After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs01 \, \times \, \sim0\farcs02$), the ring width is $\sim$3.99$\pm$0.94\,au.
 
@@
 
-***HASTA AQUI LLEGUE*****
 \section{Parametric radiative transfer model} \label{sec:model}
@@
 
-The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where the innermost small-dust ring of the parametric model hides under the artificial coronagraph.
+The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
 The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains.
@@
 The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation.
-The model reproduced the two rings that are present in the observation: the faint inner ring and the outer brighter one.
+The model reproduced the two rings that are present in the observation: the faint inner Ring13 and the outer brighter Ring24.
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.
-\ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner ring.
-Accordingly, taking the parametric model values for the large-dust inner ring we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
-For the outer ring, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$
+\ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner Ring13.
+Accordingly, taking the parametric model values for the large-dust Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
+For Ring24, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$.
 
@@
 For a ring to be stable and long-lived its horizontal dimension can not be less than its vertical height.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of the inner ring (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable.
+Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable.
 
@@
 From the similarity between the data and the resulting SED of the model we confirm that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit, this proposed ring has not been observed.
+The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit, this proposed ring (Ring6) has not been observed.
 The unexpected central emission in the 1.3\,mm continuum image could be part of this inner ring and, as it is asymmetric, the ring could be lopsided.
@@
 New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr reveals new information about its substructure.
-Using a radiative transfer model and decompositions in polar coordinates of the computed \textsc{uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
+Using a radiative transfer model and decompositions in polar coordinates of the computed {\tt uvmem}model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
 

### 2020-10-16 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
   The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present new high resolution ($\sim$20\, mas) ALMA observations of the 1.3\,mm continuum.
+We present new high resolution ($\sim$40\,mas) ALMA observations of the 1.3\,mm continuum.
 The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the RADMC3D package, allow us to propose a physical model for the source.
 The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 4.17$\pm$0.94\,au.
-Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap , and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
+Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
 The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail.
@@
 The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surpising thin Ring13 is nonetheless **15** times wider than the model scale height, and could thus be long-lived.
+The surprising thin Ring13 is nonetheless 15 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}.
-The Disks ARound T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE).
+The Disks around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE).
 The sample is not biased towards exceptionally bright and large disks, and consists of only solar-mass stars.
 A second part of the survey increased the number of sources by presenting 21 new images of circumstellar disks \citep{Garufi2020}.
-The observations revealed diversed structures and morphologies in the scattering surface of these disks.
-This letter on V4046 Sagittarii (Sgr) is part of our new DARTTS survey with ALMA (DARTTS-A) which will present millimeter observations of nine protoplanetary disks previously imaged in polarized scattered light in DARTTS-S.
+The observations revealed diverse structures and morphologies in the scattering surface of these disks.
+This letter on V4046 Sagittarii (Sgr) is part of our new DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary disks previously imaged in polarized scattered light in DARTTS-S.
 
@@
 Repeating the optimization of the disk orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share / DO NOT SHARE?
-the same orientation and centre, given the errors, and both are offset from the star.
+We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star.
 Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.
@@
 SOME FORM OF STATS WOULD BE GOOD****
-
-***I WOULD REMOVE THIS OR IDENTIFY SOMETHING CONCRETE OUT OF IT: We can compare the measured location of the inner ring according to these parameters versus to the location obtained before.
-The deviation for each azimuth is shown in Fig.
-\ref{fig:polarring}, and is not trivial since it depend on a few parameters such as the different inclinations of the rings, the difference in position angle and the shift of the centres relative to the stars.
-But even though those parameters play an important role, a possible small difference in eccentricities between the inner and the outer ring could also help explain this deviation between the two measurements.
-***
 

### 2020-10-16 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 
-For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem}package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights.
+For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights.
 The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a pure $\chi^2$ model image.
-The resulting {\tt uvmem}image shown in Fig.
+Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization.
+The resulting {\tt uvmem} image shown in Fig.
 \ref{fig:two} exhibits previously unseen substructure of the disc.
@@
 \ref{fig:polarring}).
-As the {\tt uvmem}model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), we see that Ring13 is marginally resolved.
+As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), we see that Ring13 is marginally resolved.
 After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs01 \, \times \, \sim0\farcs02$), the ring width is $\sim$3.99$\pm$0.94\,au.
@@
 \ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
-****CALCULATE THE CHI2 DIFFERENCE BETWEEN THE TWO TRACES?
-SOME FORM OF STATS WOULD BE GOOD****
+***CALCULATE THE CHI2 DIFFERENCE BETWEEN THE TWO TRACES?
+SOME FORM OF STATS WOULD BE GOOD***
 
@@
 The model environment is similar to the one used by \citet{2018MNRAS.477.5104C} for DoAr 44.
-Through trial and error, we look for a set of values for the parameters that can define a model that correctly fits the available data.
 
@@
 
-Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $\phi$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
+Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
 \begin{equation}
@@
 
+Through trial and error, we found a set of values for the parameters that define a model that correctly fits the available data.
 The final structure of the parametric model goes as Fig.
@@
 For the small dust grains, we propose a three ringed structure.
-The innermost ring of the model is located from 5 to 8\,au (Ring6),this ring is not present in the observations but was added for having a better SED fit.
+The innermost ring of the model is located from 5 to 8\,au, this ring (Ring6) is not present in the observations but was added for having a better SED fit.
 Then follows the two observed rings: the first goes from 12 to 19.5\,au (Ring13) and, with a 1\,au-wide gap between them, the outer ring (Ring24) goes from 20.5\,au and has its maximum density peak at 25\,au.
@@
 The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit, this proposed ring (Ring6) has not been observed.
-The unexpected central emission in the 1.3\,mm continuum image could be part of this inner ring and, as it is asymmetric, the ring could be lopsided.
+The unexpected central emission in the 1.3\,mm continuum image could be part of this inner ring and, as it is asymmetric, the Ring6 could be lopsided.
 
@@
 
-%\begin{table}
-% \caption{Model rings masses}
-% \label{tab:masses}
-% \begin{tabular}{lcc}
-%  \hline
-%  Ring & Location & Mass\\
-%   & $\mathrm{au}$ & $M_{\earth}$ \\
-%  \hline
-%  First & 5 to 8 & 0.0007 \\
-%  Second & 11 to 19 & 2.9 \\
-%  Third & 20 to 80 & 43 \\
-%  \hline
-% \end{tabular}
-%\end{table}
-
 \section{Conclusions} \label{sec:Conclusions}
@@
 New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr reveals new information about its substructure.
-Using a radiative transfer model and decompositions in polar coordinates of the computed {\tt uvmem}model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
+Using a radiative transfer model and decompositions in polar coordinates of the computed {\tt uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
 

### 2020-10-16 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 \ref{fig:two}).
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.
 
@@
 Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.
-\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
-***CALCULATE THE CHI2 DIFFERENCE BETWEEN THE TWO TRACES?
-SOME FORM OF STATS WOULD BE GOOD***
+\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.***
 
@@
 The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation.
-The model reproduced the two rings that are present in the observation: the faint inner Ring13 and the outer brighter Ring24.
+The model reproduced the two visible rings: the faint inner Ring13 and the outer brighter Ring24.
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.
 \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner Ring13.
-Accordingly, taking the parametric model values for the large-dust Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
+Accordingly, taking the parametric model values for Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
 For Ring24, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$.
@@
   \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au.
-The location of this ring is similar to the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
 Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.
@@
   \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.
-
-%\item The inner ring may not be totally resolved as its width is comparable to the beam size. Future observation with smaller beams sizes could give an answer on the real radial extent of the ring.
 

### 2020-10-16 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs06$, and the small orange ellipse shows an estimated {\tt uvmem} beam size of: $\sim0\farcs01 \, \times \, \sim0\farcs02$.
+The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs04 \, \times \, 0\farcs06$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs01 \, \times \, \sim0\farcs02$).
 The inset zooms into the central emission, and the green star marks the star positions.

### 2020-10-17 Draft_V4046Sgr_mnras.tex
SC edits will it finally work?

@@
 Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system.
+This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:***} below).
+If so, then given that the binary phase at the time of the observations is PA=***, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.
 
@@
 
-\citet{dOrazi} reported a binary phase in the scattered-light observation around 106\,$\degr$, setting $\phi=$0 from the North and increasing clockwise.
-Using this measurement, the binary phase was calculated at the time of the ALMA observation at $\phi=$13\,$\degr$.
-There is no clear signal of any shadow similar to the ones present in the DPI image, this could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
+The binary phase reported by \citet{dOrazi}  in the scattered-light observation is at a position angle (PA) of 360-106\,$\degr$, east of north.
+Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 360-13\,$\degr$.
+There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
 
@@
 
-To search for a possible model that could explain the available data, we perform radiative transfer modelling with \textsc{radmc3d} \citep{Dullemond_2012}.
-Here we describe a 3D modelling framework for constructing disc structures given some parameters to characterise it.
-The model environment is similar to the one used by \citet{2018MNRAS.477.5104C} for DoAr 44.
+The multi-frequency data can be interpreted in terms of a physical
+structure using radiative transfer predictions, for which we used the
+\textsc{radmc3d} package\citep{Dullemond_2012}. The general framework
+of the parametric model that we used is similar to that in
+\citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model
+values were inspired from those in \citet{Rosenfeld_2013}.
 
 For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
-The stars were placed with a separation of 0.041\,au and oriented with a 30\,$\degr$ rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi}.
+The stars were placed at a  mutual separation of 0.041\,au, so that their center of mass coincides with the origin,  and oriented at a PA of *****  30\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi****  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi} **** GIVE ORIENTATION IN TERMS OF THE PA****
 
-Recreating the complex radial and vertical structure of the V4046\,Sgr disc is not an easy task.
-We choose to build the model by thinking the components of the disc separately and then unite them as a whole.
-Given the observations that we are using, we consider that a correct approach for this disc is using two different dust populations: larger grains that are vertically settled and dominates the disc mass and a less-abundant population of smaller grains that are distributed to larger heights from the mid-plane.
-As the gas and the small-dust population are coupled, it is important to consider the gas in the modelling process, but no line emission prediction is made.
+Reproducing  the  radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
+We  built the model in terms of the gas distribution, and with  two different dust populations: larger grains that are vertically settled and dominate the total dust mass and a  population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
 
@@
 \begin{equation}
-  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right].
+  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right],
 \end{equation}
-Where $\delta(r)$ is a parameter that indicates the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ been the surface density profile.
-$\Sigma(r)$ is defined by
+where $\delta(r)$  parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
 \begin{equation}
@@
 
-We define the parametric scale height profiles for the gas and for each dust population as
+The parametric scale height profiles for the gas and for each dust population are 
 \begin{equation}
@@
 \end{equation}
-where $H_o$ is the scale height at r = $r_o$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-For the gas and the micron-sized grains $\chi$ = 1 and for the millimetre-size dust population, as \citet{Rosenfeld_2013}, we assign a fixed $\chi$ = 1/2 for simplicity.
+where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
+For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.
 
-The small-dust density distribution follows the same behaviour as the gas but with different scaling factors: the dust-to-gas ratio ($\zeta$ = 0.047 as \citet{Rosenfeld_2013}), the mass fraction between small and large dust particles ($f_{\mathrm{mass}}$) and another $\delta_{\mathrm{sd}}(r)$ factor for fine tuning that depends on the radius.
-So it is
+For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
+***explicar que es varphi y como se transforma en psi**** Our model uses the same values, with two   different flaring indeces $\psi$.
+The separation between the two values was set at $r$ = 19\,au with $\psi=0.2$ for  Ring6 and Ring13, and $\psi=0.5$ for Ring24.
+The scale height is  $H_\circ = 0.045$ at $r_0 = 19.5$\,au.
+
+The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=***$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$.
+The small dust density is thus given by
 \begin{equation}
-\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{mass}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
+\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
 \end{equation}
+***I changed $f_{\mathrm{sd}}$  to $f_{\mathrm{sd}}$. say how much is $f_{sd}$.
 
-Since the large-dust grains are less coupled to the gas, their distribution has some important differences.
-A large inner cavity and another scaling factor (or filter) is needed to generate the larger gap between the rings.
+Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and   scaling factors that account for  the larger gap between the rings.
 For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$.
-The greatest difference is in the outer ring, where we used a sum of an exponential correction with a Gaussian function and, between 32 and 34.5\,au, in an effort to recreate the break seen in the profile, we chose a different value for $\gamma$ = -8.
-So, for the large dust grains, the surface density is
-
+The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two    Gaussian profiles.
+In an effort to recreate the break seen in the outer ring between 32 and 34.5\,au, we chose a different value for $\gamma$ = -8.
+For the large dust grains the surface density profile is thus
 \begin{multline}
-  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
+  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma}  \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] +  \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
 \end{multline}
 
-Also for both dust populations, the inner part of the outer ring follows a different behaviour. The surface density profile is multiplied by an additional factor
+***REWORD PARA, IT IS NOT CLEAR WHERE DOES THIS EPSILON ENTERS - IF IT IS COMMON TO BOTH SPECIES, THEN INCLUDE IT IN THE GAS PROFILE.
+I DID NOT CHECK REDACTION, MAKE THIS AS COMPACT AS POSSIBLE***  Also for both dust populations, the inner part of the outer ring follows a different behaviour.
+The surface density profile is multiplied by an additional factor
 \begin{equation}
@@
 
-The two different populations of dust grains vary in size, the small grains range from 0.4 to 1.5\,$\micron$ and the large dust grains range from 0.4\,$\micron$ to 10\,mm.
-For absorption and opacities of dust populations we assume a typical ISM mineralogical composition, containing 70\% silicate and 30\% graphite.
+The two different populations of dust grains corresponds to  the small grains, with  radii ranging  from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii  from 0.4\,$\micron$ to 10\,mm.
+We computed the dust opacities using the {\tt bhmie} code, with  a mix composed of  70\% silicate and 30\% graphite.
 
-In an effort to obtain a similar asymmetry as the one observed in the DPI image, the simulated image at 1.65\,$\micron$ had to be taken using a special grain size distribution.
-Our approach was using a Gaussian size distribution centred at 0.4\,$\micron$, smearing out the grain size by 30\% in both directions and using 20 grain size samples in that range.
+The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function.
+In order to reproduce a similar  asymmetry, we required much larger grains that typically used in the RT modeling of  such near-IR data \citep[e.g.][]{2018MNRAS.477.5104C}.
+
+The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:two} was
+obtained with the scattering matrix calculated by the {\tt makeopac.py}
+script provided in the RADMC3D package. We used a  Gaussian size distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within  that range.
 
@@
 	\includegraphics[width=\columnwidth]{allprofiles.png}
-    \caption{Top panel shows the surface density profiles for the gas, the large and small grain populations.
-Bottom panel shows the scale height $h(r)$ as a function of polar radius.
-The dashed lines crossing both panels are the radii that confine the structures.}
+        \caption{{\bf Top:}  surface density profiles for the gas, the large and small grain populations.
+{\bf Bottom:}  scale height profile $h(r)$.
+The dashed lines crossing both panels correspond to transition  radii in the parametric model.}
     \label{fig:profiles}
@@
 
-Through trial and error, we found a set of values for the parameters that define a model that correctly fits the available data.
+Through trial and error, we found a set of values for the parameters that  correctly fit the available data.
 The final structure of the parametric model goes as Fig.
 \ref{fig:profiles} shows.
-The inner radius of the model grid was set to 0.1\,au and an otter radius of 115\,au, large enough for the dust disc to become undetectable.
+The inner radius of the model grid was set to 0.1\,au and an outter radius of 115\,au, large enough for the dust disc to become undetectable.
 
-The dust begins at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}.
+The gas and small dust surface density profiles  begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$****.
 For the small dust grains, we propose a three ringed structure.
-The innermost ring of the model is located from 5 to 8\,au, this ring (Ring6) is not present in the observations but was added for having a better SED fit.
-Then follows the two observed rings: the first goes from 12 to 19.5\,au (Ring13) and, with a 1\,au-wide gap between them, the outer ring (Ring24) goes from 20.5\,au and has its maximum density peak at 25\,au.
-The small-dust density then then fades as the radius increases.
+The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS  observations but was required to account for the  SED.
+Then follow the two  rings observed by IRDIS:  Ring13, from 12 to 19.5\,au, which is surrounded by very narrow  1\,au-wide gap, and then Ring24, that starts  20.5\,au and has its maximum density peak at 25\,au.
+The small-dust density  then decays exponentially with  radius.
 
-On the other hand, in order to reproduce the two ringed observed morphology of the millimetre continuum emission we required a model that has its large-dust grain population distributed with a wide central cavity (r = 12.3\,au), a narrow 2.6\,au-wide inner ring (Ring13) followed by a gap of 8.2\,au that separates both rings and then an outer ring (Ring24) that goes from 23\,au and has it density peak at 27.3\,au.
-This last ring has a break between 32 and 34.5\,au and then reaches out to 57\,au.
-
-For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-For that matter, the model uses two different flaring index $\psi$.
-The separation between the two values was set at $r$ = 19\,au with values of 0.2 for the Ring6 and Ring13 and 0.5 for Ring24.
-Also, the scale height is calculated using $H_o$ = 0.045 and $r_0$ = 19.5\,au.
+On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 12.3$\,au), a narrow 2.6\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap  that separates the  outer ring (Ring24), which starts at  23\,au and reaches peak  densities  at 27.3\,au.
+This last ring has an observed break between 32 and 34.5\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
+We also truncated  the model large-grain density at  $\sim$57\,au.
 
@@
 
-The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation.
-The model reproduced the two visible rings: the faint inner Ring13 and the outer brighter Ring24.
+The simulated 1.3\,mm continuum image  reproduces the two observed rings: the faint Ring13 and the  brighter Ring24.
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.
-\ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$.
-For Ring24, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$.
+\ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of  Ring13.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 2.6\,au, and a  scale height ranging from 0.25 to 0.32\,au.
+The total dust mass of Ring13 is  about 3\,M$_{\earth}$ in the model.
+In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then  breaks  at $\sim$35\,au, as in the observations, and has a total dust  mass of $\sim$43\,M$_{\earth}$.
 
-As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring can be analysed comparing its height to its radial extent.
-For a ring to be stable and long-lived its horizontal dimension can not be less than its vertical height.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height, meaning that it is stable.
+****DISCUTIR EL ANCHO OBSERVADO VS. ANCHO MODELO****
 
-Fig.
-\ref{fig:SED} shows the SED constructed from the model compared to the photometry data available in the literature in \citet{Jensen_97} and online in \textsc{vizier} and \textsc{diana}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum.
-From the similarity between the data and the resulting SED of the model we confirm that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit, this proposed ring (Ring6) has not been observed.
-The unexpected central emission in the 1.3\,mm continuum image could be part of this inner ring and, as it is asymmetric, the Ring6 could be lopsided.
+As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent ***HOW MUCH SMALLER?***.
+Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height.
+
+***CHECK THAT THE RT PREDICTIONS USE THE SAME BEAM FOR CONVOLUTION AS THE DATA, AND UPDATE ALL FIGURES****
+
+The observed SED was collected from data  in \citet{Jensen_97}, in \textsc{vizier} ***FOR WHICH BANDS?***  and \textsc{diana} ***idem***, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum.
+***THIS SHOULD GO IN SEC.
+OBS****
+
+The observed SED is compared with the model in Fig.
+\ref{fig:SED}.
+From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
+The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit ***WHERE in LBDA?****, and we may have detected this ring in the ALMA image, if this ring is  lopsided or shadowed by the secondary.
 
@@
 	\includegraphics[width=\columnwidth]{SED_.png}
-    \caption{The SED (black points and solid red curve) compared with the model (blue).
+    \caption{The observed SED of V4046\,Sgr  (black points and solid red curve) compared with the model (blue).
 The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
@@
 
-New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr reveals new information about its substructure.
-Using a radiative transfer model and decompositions in polar coordinates of the computed {\tt uvmem} model image, we measured and analysed the previously unseen thin inner ring and studied the small-dust population distribution.
-
-The key conclusions of our analysis are as follows.
+New ALMA 1.3\,mm continuum imaging of the circumbinary disc around V4046\,Sgr were analysed in the context of the available IR imaging and the observed spectral energy distribution using a RT model.
+The key conclusions are as follows.
 \begin{enumerate}
 
-  \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$.
-Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.
+\item We report the detection of a narrow ring in the 1.3\,mm continuum, with a  radius 13.46$\pm$0.43\,au and an estimated width of 4.17$\pm$0.94\,au **UPDATE FOR NEW BEAM***.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height ***UPDATE****
 
   \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au. 
-
   \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
 
-  \item As our parametric model accounts for the SED of the system, the disc requires the existence of a sub-micron dust population close (<5\,au) to the stars.
-We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains that lies under the coronagraph of the scattered-light image.
-Additionally, the weak central emission at 1.3\,mm could be part of this ring.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars ***IS THIS NOT A CONFIRMATION OF THE INNER DIST PROPOSED BY ROSENFELD+?
+IF SO, SAY SO****.
+We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and  that lies under the coronagraph of the scattered-light image.
+The weak central emission at 1.3\,mm could be part of this ring.
 \end{enumerate}
-
-Finally, we encourage additional detailed analysis and more modelling that could give some explanations of the substructures present on the disc.
-Higher resolution observations of radio continuum may provide the opportunity to make better measurements of the rings radial extension.
-For future radiative transfer models, it might be worth adding gas, using different inclinations for the inner and outer disc and implementing hydrodynamic simulations too, especially to try to unravel the mystery of how the inner ring is so thin an stable.
 

### 2020-10-19 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
   The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present new high resolution ($\sim$40\,mas) ALMA observations of the 1.3\,mm continuum.
+We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum.
 The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the RADMC3D package, allow us to propose a physical model for the source.
-The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 4.17$\pm$0.94\,au.
+The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.87$\pm$0.94\,au.
 Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
@@
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.001$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
 It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
@@
 The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs04 \,\times \, 0\farcs06$ (in natural weights).
-**Seba, sure that the survey only used C43-8?***
+This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).
+***Seba, sure that the survey only used C43-8?***
 
@@
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs04 \, \times \, 0\farcs06$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs01 \, \times \, \sim0\farcs02$).
+The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$).
 The inset zooms into the central emission, and the green star marks the star positions.
@@
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$.
+The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$.
 For all the images in the figure the colour scale is linear.}
@@
 \ref{fig:polarring}).
-As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs04 \,\times \, 0\farcs06$), we see that Ring13 is marginally resolved.
-After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs01 \, \times \, \sim0\farcs02$), the ring width is $\sim$3.99$\pm$0.94\,au.
+As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved.
+After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.87$\pm$0.94\,au.
 
@@
 Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:***} below).
-If so, then given that the binary phase at the time of the observations is PA=***, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.
+This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
+If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.
 
-The scattered-light image shown in Fig.
-\ref{fig:two} also shows a double ring structure in the micron-sized dust distribution.
+The scattered-light image shown in Fig. \ref{fig:two} also shows a double ring structure in the micron-
+sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 
-The binary phase reported by \citet{dOrazi}  in the scattered-light observation is at a position angle (PA) of 360-106\,$\degr$, east of north.
-Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 360-13\,$\degr$.
+The binary phase reported by \citet{dOrazi}  in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north.
+Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$.
 There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
@@
 
-The multi-frequency data can be interpreted in terms of a physical
-structure using radiative transfer predictions, for which we used the
-\textsc{radmc3d} package\citep{Dullemond_2012}. The general framework
-of the parametric model that we used is similar to that in
-\citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model
-values were inspired from those in \citet{Rosenfeld_2013}.
+The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package\citep{Dullemond_2012}.
+The general framework of the parametric model that we used is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}.
 
 For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
-The stars were placed at a  mutual separation of 0.041\,au, so that their center of mass coincides with the origin,  and oriented at a PA of *****  30\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi****  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi} **** GIVE ORIENTATION IN TERMS OF THE PA****
+The stars were placed at a  mutual separation of 0.041\,au, so that their centre of mass coincides with the origin,  and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi***  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi}.
 
@@
 
-The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=***$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$.
+The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=0.01$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$.
 The small dust density is thus given by
@@
 \end{equation}
-***I changed $f_{\mathrm{sd}}$  to $f_{\mathrm{sd}}$. say how much is $f_{sd}$.
 
@@
 The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two    Gaussian profiles.
-In an effort to recreate the break seen in the outer ring between 32 and 34.5\,au, we chose a different value for $\gamma$ = -8.
+In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6.
 For the large dust grains the surface density profile is thus
@@
 
-***REWORD PARA, IT IS NOT CLEAR WHERE DOES THIS EPSILON ENTERS - IF IT IS COMMON TO BOTH SPECIES, THEN INCLUDE IT IN THE GAS PROFILE.
-I DID NOT CHECK REDACTION, MAKE THIS AS COMPACT AS POSSIBLE***  Also for both dust populations, the inner part of the outer ring follows a different behaviour.
-The surface density profile is multiplied by an additional factor
+The inner part of the outer ring follows a different behaviour. The gas density profile is multiplied by an additional factor
 \begin{equation}
@@
 
-The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:two} was
-obtained with the scattering matrix calculated by the {\tt makeopac.py}
-script provided in the RADMC3D package. We used a  Gaussian size distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within  that range.
+The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:two} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the RADMC3D package.
+We used a  Gaussian size distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within  that range.
 
@@
 \ref{fig:profiles} shows.
-The inner radius of the model grid was set to 0.1\,au and an outter radius of 115\,au, large enough for the dust disc to become undetectable.
+The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.
 
-The gas and small dust surface density profiles  begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$****.
+The gas and small dust surface density profiles  begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au.
 For the small dust grains, we propose a three ringed structure.
@@
 
-On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 12.3$\,au), a narrow 2.6\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap  that separates the  outer ring (Ring24), which starts at  23\,au and reaches peak  densities  at 27.3\,au.
-This last ring has an observed break between 32 and 34.5\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
-We also truncated  the model large-grain density at  $\sim$57\,au.
+On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 11.8$\,au), a narrow 3.6\,au-wide inner ring (which is Ring13) followed by a .2\,au gap  that separates the  outer ring (Ring24), which starts at  22\,au and reaches peak  densities  at 27.7\,au.
+This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
+We also truncated  the model large-grain density at  $\sim$55\,au.
 
@@
 \ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of  Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 2.6\,au, and a  scale height ranging from 0.25 to 0.32\,au.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 3.6\,au, and a  scale height ranging from 0.24 to 0.32\,au.
 The total dust mass of Ring13 is  about 3\,M$_{\earth}$ in the model.
@@
 
-****DISCUTIR EL ANCHO OBSERVADO VS. ANCHO MODELO****
+****DISCUTIR EL ANCHO OBSERVADO 3.87 VS. ANCHO MODELO 3.6 ****
 
-As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent ***HOW MUCH SMALLER?***.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (4.17\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height.
-
-***CHECK THAT THE RT PREDICTIONS USE THE SAME BEAM FOR CONVOLUTION AS THE DATA, AND UPDATE ALL FIGURES****
+As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent.
+Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$13 times its scale height.
 
@@
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit ***WHERE in LBDA?****, and we may have detected this ring in the ALMA image, if this ring is  lopsided or shadowed by the secondary.
+The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$***, and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary.
 
@@
 \begin{enumerate}
-
-\item We report the detection of a narrow ring in the 1.3\,mm continuum, with a  radius 13.46$\pm$0.43\,au and an estimated width of 4.17$\pm$0.94\,au **UPDATE FOR NEW BEAM***.
+  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a  radius 13.46$\pm$0.43\,au and an estimated width of 3.87$\pm$0.94\,au.
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height ***UPDATE****
+Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$13 times its estimated height.
 
   \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.
+
   \item We interpret the asymmetry observed with SPHERE-IRDIS at 1.65\,$\micron$ as due to strong forward-scattering, which implies that the dust population is depleted of grains smaller than $\sim$0.4\,$\micron$.
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars ***IS THIS NOT A CONFIRMATION OF THE INNER DIST PROPOSED BY ROSENFELD+?
-IF SO, SAY SO****.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars.
 We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and  that lies under the coronagraph of the scattered-light image.

### 2020-10-20 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 The resulting {\tt uvmem} image shown in Fig.
-\ref{fig:two} exhibits previously unseen substructure of the disc.
+\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
 This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
@@
 For all the images in the figure the colour scale is linear.}
-  \label{fig:two}
+  \label{fig:images_vs_simulated}
 \end{figure*}
@@
 Ring13 is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig.
-\ref{fig:two}).
+\ref{fig:images_vs_simulated}).
 We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.
@@
 Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.
-\ref{fig:two}).
+\ref{fig:images_vs_simulated}).
 Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
@@
 
-The scattered-light image shown in Fig. \ref{fig:two} also shows a double ring structure in the micron-
+The scattered-light image shown in Fig. \ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
 sized dust distribution.
@@
 
+The observed SED was collected from data  in \citet{Jensen_97}, in \textsc{vizier} and \textsc{diana}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}.).
+***
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{SED_.png}
+    \caption{The observed SED of V4046\,Sgr  (black points and solid red curve) compared with the model (blue).
+The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
+The dashed silver curve shows the emission of the stellar photosphere model.}
+    \label{fig:SED}
+\end{figure}
+
 \section{Parametric radiative transfer model} \label{sec:model}
@@
 For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
-The stars were placed at a  mutual separation of 0.041\,au, so that their centre of mass coincides with the origin,  and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by d'Orazzi***  rotation, relative to the semi-major axis of the disk, to match the shadows reported by \citet{dOrazi}.
+The stars were placed at a  mutual separation of 0.041\,au, so that their centre of mass coincides with the origin,  and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
 
@@
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-***explicar que es varphi y como se transforma en psi**** Our model uses the same values, with two different flaring indeces $\psi$.
+***explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indeces $\psi$.
 The separation between the two values was set at $r$ = 19\,au with $\psi=0.2$ for  Ring6 and Ring13, and $\psi=0.5$ for Ring24.
@@
 The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar  asymmetry, we required much larger grains that typically used in the RT modeling of  such near-IR data \citep[e.g.][]{2018MNRAS.477.5104C}.
+In order to reproduce a similar  asymmetry, we required much larger grains that typically used in the RT modelling of  such near-IR data \citep[e.g.][]{2018MNRAS.477.5104C}.
 
-The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:two} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the RADMC3D package.
+The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the RADMC3D package.
 We used a  Gaussian size distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within  that range.
@@
 
-On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 11.8$\,au), a narrow 3.6\,au-wide inner ring (which is Ring13) followed by a .2\,au gap  that separates the  outer ring (Ring24), which starts at  22\,au and reaches peak  densities  at 27.7\,au.
+On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a .2\,au gap  that separates the  outer ring (Ring24), which starts at  22\,au and reaches peak  densities  at 27.7\,au.
 This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
@@
 
-Our parametric model is fairly successful in reproducing the available data. The simulated images and the SED of the model are shown in Fig. \ref{fig:two} and Fig. \ref{fig:SED} respectively.
+Our parametric model is fairly successful in reproducing the available data.
+The simulated images and the SED of the model are shown in Fig.
+\ref{fig:images_vs_simulated} and Fig.
+\ref{fig:SED} respectively.
 
@@
 \ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of  Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 3.6\,au, and a  scale height ranging from 0.24 to 0.32\,au.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 3.7\,au, and a  scale height ranging from 0.24 to 0.32\,au.
 The total dust mass of Ring13 is  about 3\,M$_{\earth}$ in the model.
@@
 
-****DISCUTIR EL ANCHO OBSERVADO 3.87 VS. ANCHO MODELO 3.6 ****
+***DISCUTIR EL ANCHO OBSERVADO (3.87) VS. ANCHO MODELO (3.7) ***
 
@@
 Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$13 times its scale height.
-
-The observed SED was collected from data  in \citet{Jensen_97}, in \textsc{vizier} ***FOR WHICH BANDS?***  and \textsc{diana} ***idem***, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum.
-***THIS SHOULD GO IN SEC.
-OBS****
 
@@
 The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$***, and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{SED_.png}
-    \caption{The observed SED of V4046\,Sgr  (black points and solid red curve) compared with the model (blue).
-The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum.
-The dashed silver curve shows the emission of the stellar photosphere model.}
-    \label{fig:SED}
-\end{figure}
 

### 2020-10-21 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
 We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum.
-The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the RADMC3D package, allow us to propose a physical model for the source.
-The new ALMA data reveal a very fine ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.87$\pm$0.94\,au.
+The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source.
+The new ALMA data reveal a very thin ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.87$\pm$0.94\,au.
 Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
 The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail.
-The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disk.
+The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
 Faint mm-continuum coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary.
 The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surprising thin Ring13 is nonetheless 15 times wider than the model scale height, and could thus be long-lived.
+The surprising thin Ring13 is nonetheless roughly 15 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 
-Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimeter/submillimetre Array (ALMA) or with VLT/SPHERE has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}.
-The Disks around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE).
-The sample is not biased towards exceptionally bright and large disks, and consists of only solar-mass stars.
-A second part of the survey increased the number of sources by presenting 21 new images of circumstellar disks \citep{Garufi2020}.
-The observations revealed diverse structures and morphologies in the scattering surface of these disks.
-This letter on V4046 Sagittarii (Sgr) is part of our new DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary disks previously imaged in polarized scattered light in DARTTS-S.
+Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
+%VLT/SPHERE 
+the current generation of high-contrast images 
+has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}.
+The discs around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE) \citep{2019A&A...631A.155B}.
+The sample is not biased towards exceptionally bright and large discs, and consists of only solar-type stars.
+A second part of the survey increased the number of sources by presenting 21 new images of circumstellar discs \citep{Garufi2020}.
+The observations revealed diverse structures and morphologies in the scattering surface of these discs.
+This letter on V4046 Sagittarii (Sgr) is part of the DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
 
@@
 This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).
-***Seba, sure that the survey only used C43-8?***
 
@@
 
-Ring13 is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig.
+Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.
 \ref{fig:images_vs_simulated}).
@@
 
-Repeating the optimization of the disk orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
+Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
 We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star.
 Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.
-\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.***
+\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
 
@@
 Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$.
-There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disk cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
+There is no hint of  radio decrements  in  either Rings13 nor  in Ring24 that would match shadowing at this PA,   could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
 
@@
 
-The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package\citep{Dullemond_2012}.
+The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep{Dullemond_2012}.
 The general framework of the parametric model that we used is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}.
@@
 \begin{equation}
-  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \,r H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{r H(r)}\right)^2\right],
+  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)}  \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
 \end{equation}
@@
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-***explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indeces $\psi$.
-The separation between the two values was set at $r$ = 19\,au with $\psi=0.2$ for  Ring6 and Ring13, and $\psi=0.5$ for Ring24.
+explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indexes $\psi$.
+The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for  Ring6 and Ring13, and $\psi=0.5$ for Ring24.
 The scale height is  $H_\circ = 0.045$ at $r_0 = 19.5$\,au.
 
-The small-dust density distribution follows the same behaviour as the gas, with a dust-to-gas mass ratio $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}, the mass fraction between small and large dust particles $f_\mathrm{sd}=0.01$ and another factor for fine tuning that depends on the radius,  $\delta_{\mathrm{sd}}(r)$.
-The small dust density is thus given by
+The total dust-to-gas mass ratio is taken to be $\zeta = 0.047$ \citep[as in][]{Rosenfeld_2013}.
+The small dust grains are assumed to only make up for a fraction of $f_\mathrm{sd}=1\%$ of the total dust mass.
+As small dust is typically tightly coupled to the gas dynamics, its density profile is largely expected to follow the gas density.
+To allow for local deviations we introduce the function $\delta_{\mathrm{sd}}(r)$.
+Then the density of small dust can be calculated as:
 \begin{equation}
@@
 The two different populations of dust grains corresponds to  the small grains, with  radii ranging  from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii  from 0.4\,$\micron$ to 10\,mm.
-We computed the dust opacities using the {\tt bhmie} code, with  a mix composed of  70\% silicate and 30\% graphite.
+We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with  a mix composed of  70\% silicate and 30\% graphite.
 
 The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar  asymmetry, we required much larger grains that typically used in the RT modelling of  such near-IR data \citep[e.g.][]{2018MNRAS.477.5104C}.
+In order to reproduce a similar  asymmetry, we used much larger grains that typically used in the RT modelling of  such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
 
-The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the RADMC3D package.
-We used a  Gaussian size distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within  that range.
+The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
+Only for this image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within that range.
 
@@
 On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a .2\,au gap  that separates the  outer ring (Ring24), which starts at  22\,au and reaches peak  densities  at 27.7\,au.
-This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with the a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
+This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
 We also truncated  the model large-grain density at  $\sim$55\,au.
@@
 \ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of  13.6\,au,  a  width of 3.7\,au, and a  scale height ranging from 0.24 to 0.32\,au.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au,  a  width of 3.7\,au, and a scale height of the millimetre-size dust ranging from 0.24 to 0.32\,au.
 The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model.
 In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks  at $\sim$35\,au, as in the observations, and has a total dust  mass of $\sim$43\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the location of the ring, and a 0.17\,au difference in the width estimation.***
 
-***DISCUTIR EL ANCHO OBSERVADO (3.87) VS. ANCHO MODELO (3.7) ***
-
-As \citet{2018ApJ...869L..46D} explains, the stability of a narrow dust ring requires that its  height be smaller than its  radial extent.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$13 times its scale height.
+As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its  height is smaller than its radial extent.
+Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height.
 
@@
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$***, and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary.
+The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$, and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary.
 
@@
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$13 times its estimated height.
+Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is roughly 15 times its estimated height.
 
@@
 
-Try to keep it short.
+This paper makes use of the following ALMA data: ADS/JAO.ALMA \#2017.0.01167.S.
+ALMA is a partnership of ESO (representing its member states), NSF (USA) and NINS (Japan), together with NRC (Canada), MOST and ASIAA (Taiwan), and KASI (Republic of Korea), in cooperation with the Republic of Chile.
+The Joint ALMA Observatory is operated by ESO, AUI/NRAO and NAOJ.
+The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
 

### 2020-10-26 Draft_V4046Sgr_mnras.tex
Add files via upload

@@
 \usepackage{graphicx}	% Including figure files
-%% \usepackage{amsmath}	% Advanced maths commands
+\usepackage{amsmath}	% Advanced maths commands
 %% \usepackage{amssymb}	% Extra maths symbols
@@
 The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surprising thin Ring13 is nonetheless roughly 15 times wider than the model scale height, and could thus be long-lived.
+The surprising thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} in a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
 It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
@@
 The structure of this letter is as follows.
-The observations, including new 1.3\,mm continuum data, are described in Section \ref{sec:Observations}.
-We interpret the data in terms of a parametric model, presented in Section \ref{sec:model}.
+The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}.
+We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}.
 Previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but our new ALMA data bring additional information.
-Our results are discussed in Section \ref{sec:results} and summarised in Section \ref{sec:Conclusions}.
+Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.
 
@@
 The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, taken with a beam size of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).
+This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, acquired with baselines ranging from 92 to 8548\,m, which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).
 
-In this investigation, we use the polarimetric image at 1.65\,$\micron$ previously published as part of the DARTTS-SPHERE I survey \citep{Avenhaus_2018}.
-The image was taken at the ESO Very Large Telescope with the SPHERE-IRDIS instrument in differential polarization imaging (DPI) mode, and a complete description of the data reduction was presented in \citet{Avenhaus_2018}.
+V4046 Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016.
+All the details of this observation can be found in the first DARTTS-S paper \citep{Avenhaus_2018} where the image was first published.
+Here we use a new reduction of the $H$ band data produced by the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
+The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}.
+The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
+The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circum rather than inter-stellar material.
 
@@
 Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization.
-The resulting {\tt uvmem} image shown in Fig.
-\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
+The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
 This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
@@
 From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc).
+Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc).
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
@@
 
-Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.
-\ref{fig:images_vs_simulated}).
+Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}).
 We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.
@@
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth.
-On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.
-\ref{fig:polarring}).
+On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.~\ref{fig:polarring}).
 As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved.
@@
 We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star.
-Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.
-\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
+Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
 
-Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.
-\ref{fig:images_vs_simulated}).
+Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}).
 Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
@@
 
-The scattered-light image shown in Fig. \ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
+The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
 sized dust distribution.
@@
     \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
-The grey shaded area represents the inner working angle of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
+The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
     \label{fig:radprofiles}
@@
 
-The observed SED was collected from data  in \citet{Jensen_97}, in \textsc{vizier} and \textsc{diana}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}.).
-***
+The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}.).
 
@@
 The general framework of the parametric model that we used is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}.
+Through trial and error, we found a set of values for the parameters that correctly fit the available data.
+The final structure of the parametric model goes as Fig.~\ref{fig:profiles} shows.
 
@@
 
-Assuming a three dimensional model in a spherical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
+Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
 \begin{equation}
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+
+%The $\delta(r)$ function, that account for deviations from the power law, is defined as:
+%\begin{align}
+%\delta(r) = \left\{ \begin{array}{cc} 
+%                 5E-6 & \hspace{5mm} 0.3<r<5 \\
+%                 5E-3 & \hspace{5mm} 5<r<8  \\
+%                 5E-5 & \hspace{5mm} 8<r<12\\
+%                 2.5E-2 & \hspace{5mm} 12<r<19.5 \\
+%                 1E-8 & \hspace{5mm} 19.5<r<20.5 \\
+%                 1E-4 & \hspace{5mm} 20.5<r<25 \\
+%                 1.7E-1 & \hspace{5mm} 25<r<120 \\
+%                \end{array} \right.
+%\end{align}
 
@@
 As small dust is typically tightly coupled to the gas dynamics, its density profile is largely expected to follow the gas density.
-To allow for local deviations we introduce the function $\delta_{\mathrm{sd}}(r)$.
 Then the density of small dust can be calculated as:
 \begin{equation}
-\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \, \delta_{\mathrm{sd}}(r) \: \zeta .
+\rho_{\mathrm{small-dust}}(r,z)=\rho_{\mathrm{gas}}(r,z)\, f_{\mathrm{sd}} \: \zeta .
 \end{equation}
@@
 
-The inner part of the outer ring follows a different behaviour. The gas density profile is multiplied by an additional factor
+The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, the gas density profile is multiplied by an additional factor
 \begin{equation}
-    \epsilon(r) = \delta +  (1 - \delta) \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
+    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
 \end{equation}
-where $\delta=10^{-4}$ and $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring.
+where $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring.
 This parameter allow us to model a smoother inner wall of the outer ring.
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-Only for this image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared  out by 30\% in both directions, and using 20 grain size bins within that range.
+As a way of reproducing the \textit{H} band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range.
+This distribution applies only to generate the NIR image.
 
@@
 
-Through trial and error, we found a set of values for the parameters that  correctly fit the available data.
-The final structure of the parametric model goes as Fig.
-\ref{fig:profiles} shows.
-The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.
-
 The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au.
@@
 
-On the other hand, in order to reproduce the double-ringed  morphology of the millimetre continuum emission,  we required a model with   a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a .2\,au gap  that separates the  outer ring (Ring24), which starts at  22\,au and reaches peak  densities  at 27.7\,au.
+On the other hand, in order to reproduce the double-ringed morphology of the millimetre continuum emission, we required a model with a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap that separates the outer ring (Ring24), which starts at 22\,au and reaches peak densities at 27.7\,au.
 This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
@@
 
-We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section \ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A.
+The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.
+We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A.
 = 74.6\,$\degr$.
@@
 Our parametric model is fairly successful in reproducing the available data.
-The simulated images and the SED of the model are shown in Fig.
-\ref{fig:images_vs_simulated} and Fig.
-\ref{fig:SED} respectively.
+The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
 
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.
-\ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au,  a  width of 3.7\,au, and a scale height of the millimetre-size dust ranging from 0.24 to 0.32\,au.
+As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of Ring13.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au, a width of 3.7\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.28 to 0.40\,au.
 The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model.
 In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the location of the ring, and a 0.17\,au difference in the width estimation.***
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the location of the ring, and a 0.17\,au difference in the width estimation.
 
 As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section \ref{sec:Observations}), we have that its width is $\sim$15 times its scale height.
+Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.
 
-The observed SED is compared with the model in Fig.
-\ref{fig:SED}.
+The observed structure may point to the existence of planet-disk interaction within this system, where a giant planet depletes its orbit of gas and dust material.
+A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
+This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets .
+We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
+
+The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 3.87\mathrm{au}$.
+The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
+Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
+Assuming that the gas' Ring13-width in the RT model corresponds to the FWHM of a Gaussian structure $w_\mathrm{g} = 7.5\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+
+Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
+\begin{equation}\label{eq:ringwidth}
+        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
+\end{equation}
+where we implicitly assumed the turbulent diffusivity to be equal to the turbulent viscosity.
+Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number.
+Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda \mathrm{obs}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
+With these considerations, equation (\ref{eq:ringwidth}) provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity.
+We emphasise that this relies on rough estimates and is additionally restricted to the area within R13.
+
+The observed SED is compared with the model in Fig.~\ref{fig:SED}.
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
@@
 The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is roughly 15 times its estimated height.
+Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is roughly 12 times its estimated height.
 
@@
 The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
+
+This research has made use of the VizieR catalogue access tool, CDS, Strasbourg, France (DOI : 10.26093/cds/vizier).
+The original description of the VizieR service was published in \citet{2000A&AS..143...23O}.
+
+This research has made use of the NASA/IPAC Infrared Science Archive, which is funded by the National Aeronautics and Space Administration and operated by the California Institute of Technology.
 

### 2020-11-26 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

@@
   The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present new high resolution ($\sim$20\,mas) ALMA observations of the 1.3\,mm continuum.
+We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum.
 The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source.
-The new ALMA data reveal a very thin ring at a radius of 13.46$\pm$0.43\,au (Ring13), with a marginally resolved radial width of 3.87$\pm$0.94\,au.
-Ring13 is the brightest structure in scattered-light, where it is surrounded by a $\sim$9\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
-The steeply decreasing radial slope of Ring24 breaks at $\sim$35\,au into a shallow tail.
+The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
+Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
+The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
 The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
-Faint mm-continuum coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary.
+Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA.
+***
+  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
   The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surprising thin Ring13 is nonetheless roughly 12 times wider than the model scale height, and could thus be long-lived.
+The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 
-Recent observations of young circumstellar discs have transformed current knowledge of planet formation, but the focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
+Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
+The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
 %VLT/SPHERE 
@@
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} in a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
 It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
@@
 The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
-The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circum rather than inter-stellar material.
+The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
 
@@
 The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a $\chi^2$ model image with $\lambda$ = 0.1 for regularization.
+Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits**).
 The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
@@
 The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail.
-While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between
-$\sim$10 and 17\,au.
+While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.
 
@@
 From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc).
+Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs077 \, \times \, 0\farcs051$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs026 \, \times \, \sim0\farcs017$).
+The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$).
 The inset zooms into the central emission, and the green star marks the star positions.
@@
 Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The orange ellipse shows the size of the beam: $0\farcs026 \, \times \, 0\farcs017$.
+The orange ellipse shows the size of the beam: $0\farcs035 \, \times \, 0\farcs031$.
 For all the images in the figure the colour scale is linear.}
@@
 Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}).
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 77.31$\pm$0.03\,$\degr$, an inclination of 32.96$\pm$0.02\,$\degr$ and a centre at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas, relative to the stars.
 
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth.
-On average, we obtained a FWHM of 4.17$\pm$0.94\,au, and a stellocentric radius of 13.46$\pm$0.43\,au (See Fig.~\ref{fig:polarring}).
-As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs077 \,\times \, 0\farcs051$), we see that Ring13 is marginally resolved.
-After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs026 \, \times \, \sim0\farcs016$), the ring width is $\sim$3.87$\pm$0.94\,au.
+On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
+As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved.
+After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.
 
-Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star.
-Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, perhaps due to the joint effect of all these small differences.
+Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.*** %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
+Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.
 
@@
 Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
+This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+***
+%match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
 If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.
 
-The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-
-sized dust distribution.
+The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 
-The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 254\,$\degr$, east of north.
-Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of 347\,$\degr$.
-There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA, could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
+The binary phase reported by \citet{dOrazi} in the scattered-light observation is at a position angle (PA) of 265\,$\degr$, east of north.
+Using this measurement, the binary phase was calculated at the time of the ALMA observation at a PA of $\sim$80\,$\degr$.
+There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA.
+This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
 
@@
 
-\begin{figure}
-	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
-    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
-The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
-    \label{fig:radprofiles}
-\end{figure}
-
-The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.\ref{fig:SED}.).
+The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.~\ref{fig:SED}).
+The SED will provide us with missing information about the dust population.
 
@@
 
-For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of log$\,\dot{\mathrm{M}} = -$9.3\,Myr$^{-1}$ for both cases \citep{10.1111/j.1365-2966.2011.19366.x}.
+For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 \begin{equation}
-  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
+  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
 \end{equation}
-where $\delta(r)$ parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
-\begin{equation}
-  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
-\end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-
-%The $\delta(r)$ function, that account for deviations from the power law, is defined as:
-%\begin{align}
-%\delta(r) = \left\{ \begin{array}{cc} 
-%                 5E-6 & \hspace{5mm} 0.3<r<5 \\
-%                 5E-3 & \hspace{5mm} 5<r<8  \\
-%                 5E-5 & \hspace{5mm} 8<r<12\\
-%                 2.5E-2 & \hspace{5mm} 12<r<19.5 \\
-%                 1E-8 & \hspace{5mm} 19.5<r<20.5 \\
-%                 1E-4 & \hspace{5mm} 20.5<r<25 \\
-%                 1.7E-1 & \hspace{5mm} 25<r<120 \\
-%                \end{array} \right.
-%\end{align}
+where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.
 
@@
     \label{scale}
-  H(r)=\chi \, H_{o}(r) \, [r/r_{o}(r)]^{\psi(r)},
+  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
 \end{equation}
@@
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-explicar que es varphi y como se transforma en psi*** Our model uses the same values, with two different flaring indexes $\psi$.
+Our model uses the same values, with two different flaring indexes $\psi$.
 The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 0.045$ at $r_0 = 19.5$\,au.
+The scale height is $H_\circ = 1$\,au at $r_\circ = 19$\,au.
+
+We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. Then it is defined by:
+\begin{equation}
+  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
+\end{equation}
+
+The inner disk follows a power law function defined by
+\begin{equation}
+  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
+\end{equation}
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.6\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
+
+We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
+\begin{equation}
+  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
+  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
+\end{equation}
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=6$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=1\times10^{13}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.
+
+For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
+\begin{equation}
+  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
+\end{equation}
+with $\delta_{\mathrm{sd}}$ = 5.2$\times 10^4$.
+But the inner wall of Ring24 follows a different behaviour.
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
+\begin{equation}
+    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
+\end{equation}
+This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 19.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.6\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
 
@@
 
-Since the large-dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings.
-For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$.
-The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles.
-In an effort to recreate the break seen in the outer ring between 30.2 and 36.7\,au, we chose a different value for $\gamma$ = -6.
-For the large dust grains the surface density profile is thus
-\begin{multline}
-  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
-\end{multline}
+Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
+We also truncated the model large-grain density at 64\,au.
+The large-dust surface density profile is defined by the sum of its two components
+\begin{equation}
+  \Sigma_{\mathrm{ld}}(r) = 
+  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
+\end{equation}
 
-The inner part of the outer ring follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, the gas density profile is multiplied by an additional factor
+For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.36$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=4.2\times10^{13}$.
+For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au.
+Thus, the surface density of the outer ring of large grains dust is defined by
 \begin{equation}
-    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3,
+    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
 \end{equation}
-where $R_\mathrm{in}$ and $R_\mathrm{peak}$ would depend on the dust population, marking the beginning and the maximum density peak of the outer ring.
-This parameter allow us to model a smoother inner wall of the outer ring.
+where
+\begin{equation}
+  \delta_{\mathrm{ld}}(r) =
+  \begin{cases}
+  0                 & r < 24.6\text{\,au} \\
+  4.37 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
+  2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
+  1.82 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  \end{cases}
+\end{equation}
+Then the final density of large dust can be calculated as
+\begin{equation}
+\rho_{\mathrm{large-dust}}(r,z)=
+\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
+\end{equation}
 
-The two different populations of dust grains corresponds to the small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and the large dust grains range, with radii from 0.4\,$\micron$ to 10\,mm.
+The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
 We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 70\% silicate and 30\% graphite.
@@
 The observed near-far asymmetry in the DPI image is suggestive of a strongly forward-scattering phase function.
-In order to reproduce a similar asymmetry, we used much larger grains that typically used in the RT modelling of such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
+In order to reproduce a similar asymmetry, we used much larger grains than typically used in the RT modelling of such near-IR data \citep[e.g.,][]{2018MNRAS.477.5104C}.
 
-The simulated DPI image at 1.65\,$\micron$ in Fig.\,\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H} band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range.
+The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range.
 This distribution applies only to generate the NIR image.
@@
         \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations.
-{\bf Bottom:} scale height profile $h(r)$.
+{\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
 The dashed lines crossing both panels correspond to transition radii in the parametric model.}
@@
 
-The gas and small dust surface density profiles begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.1\,au.
-For the small dust grains, we propose a three ringed structure.
-The innermost ring of the model is located from 5 to 8\,au, this ring, introduced as Ring6 in Sec.\,\ref{sec:Observations}, is not detectable in the IRDIS observations but was required to account for the SED.
-Then follow the two rings observed by IRDIS: Ring13, from 12 to 19.5\,au, which is surrounded by very narrow 1\,au-wide gap, and then Ring24, that starts 20.5\,au and has its maximum density peak at 25\,au.
-The small-dust density then decays exponentially with radius.
-
-On the other hand, in order to reproduce the double-ringed morphology of the millimetre continuum emission, we required a model with a wide central cavity ($r = 11.7$\,au), a narrow 3.7\,au-wide inner ring (which is Ring13) followed by a 8.2\,au gap that separates the outer ring (Ring24), which starts at 22\,au and reaches peak densities at 27.7\,au.
-This last ring has an observed break between 30.2 and 36.7\,au, which is reproduced in the model with a discontinuity in the exponent $\gamma$, along with the sum of the decaying exponentials.
-We also truncated the model large-grain density at $\sim$55\,au.
-
-The inner radius of the model grid was set to 0.1\,au and an outer radius of 115\,au, large enough for the dust disc to become undetectable.
-We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 33.9\,$\degr$ and a P.A.
-= 74.6\,$\degr$.
+The inner radius of the model grid was set to 0.1\,au and an outer radius of 100\,au, large enough for the dust disc to become undetectable.
+We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+= 77.31\,$\degr$.
 Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.
@@
 
-Our parametric model is fairly successful in reproducing the available data.
+While certainly not unique, our parametric model is fairly successful in reproducing the available data.
 The simulated images and the SED of the model are shown in Fig.~\ref{fig:images_vs_simulated} and Fig.~\ref{fig:SED} respectively.
@@
 
+\begin{figure}
+	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
+    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
+The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
+    \label{fig:radprofiles}
+\end{figure}
+
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides an approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.6\,au, a width of 3.7\,au, and a scale height FWHM of the millimetre-size dust ranging from 0.28 to 0.40\,au.
-The total dust mass of Ring13 is about 3\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$35\,au, as in the observations, and has a total dust mass of $\sim$43\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.14\,au difference in the location of the ring, and a 0.17\,au difference in the width estimation.
-
-As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent.
-Using the parametric model scale height of 0.28\,au at 13.46\,au and the measured width of Ring13 (3.87\,au FWHM, see Section~\ref{sec:Observations}), we have that its width is $\sim$12 times its scale height.
+As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13.
+Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
+The total dust mass of Ring13 is about 1.5\,M$_{\earth}$ in the model.
+In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$49\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.04\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
+%As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
+Using the large grains scale height of 0.66\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$2.3 times more extended in radial than in vertical direction.
 
@@
 A possible constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
-This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets .
-We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
+As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
+This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
+%We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 3.87\mathrm{au}$.
+The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
 The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
 Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
-Assuming that the gas' Ring13-width in the RT model corresponds to the FWHM of a Gaussian structure $w_\mathrm{g} = 7.5\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 4.83\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
@@
 Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda \mathrm{obs}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
-With these considerations, equation (\ref{eq:ringwidth}) provides a value of $\alpha \approx 0.01$ for the level of turbulent viscosity.
-We emphasise that this relies on rough estimates and is additionally restricted to the area within R13.
+Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
+With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity.
+We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
+Yet, its moderate value agrees with the limit \citet{2018ApJ...869L..46D} inferred from multiple dust rings at larger orbital distances ($\alpha \gtrsim 5\times10^{-4}$).
+Further, it is also consistent with the non-detection of non-thermal broadening of CO lines reported by \citet{Flaherty_2020}, from which the authors deduced an upper limit of $\alpha \lesssim 10^{-3}$ at the midplane of V4046\,Sgr.
 
@@
 From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$, and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary.
+The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$.
+%and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
+Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would have to have millimetre-size dust grains due to dust trapping, and those grains are not present in the ALMA observation.
+***
 
@@
 \begin{enumerate}
-  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.46$\pm$0.43\,au and an estimated width of 3.87$\pm$0.94\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 3\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is roughly 12 times its estimated height.
+  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.5\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.66\,au at 13.32\,au) we have that the ring width is roughly 2.3 times its estimated height.
 
-  \item The 1.3\,mm outer ring, that starts at $\sim$23\,au and has its peak intensity at $\sim$32\,au, presents a visible break in the surface brightness at $\sim$35\,au.
+  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$35\,au.
 
@@
   \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars. 
-We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and that lies under the coronagraph of the scattered-light image.
-The weak central emission at 1.3\,mm could be part of this ring.
+  %We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and that lies under the coronagraph of the scattered-light image. 
+  %The weak central emission at 1.3\,mm could be part of this ring.
 \end{enumerate}

### 2020-11-27 Draft_V4046Sgr_mnras.tex
SC editions

@@
 Sebasti\'an P\'erez,$^{2}$
-et al. 
+Antonio Hales,$^{3}$
+Philipp Weber, $^{1,2}$ \newauthor
+Carla Arce-Tord,
+Lucas Cieza,
+Antonio Garufi,
+Sebasti\'an Marino,
+Alice Zurlo
 \\
@@
 \begin{abstract}
-  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present new high resolution ($\sim$50\,mas) ALMA observations of the 1.3\,mm continuum.
-The comparison of these observations, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), against radiative transfer (RT) predictions carried out with the \textsc{radmc3d} package, allow us to propose a physical model for the source.
-The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
-Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very bright mm outer ring (Ring24) with a sharp inner edge at 24\,au.
-The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
-The RT model requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc.
-Faint mm-continuum close ($\sim0\farcs02$) to the stellar position is picked up by ALMA.
-***
-  %coincident with Ring6 is picked up by ALMA, whose morphology suggests that Ring6 is lopsided or shadowed by the secondary. 
-  The previously reported scattered-light shadow of the secondary star is also reproduced by the RT model.
-The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived.
-The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
+  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc
+  known for its wide cavity and dusty ring.  We present high
+  resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm
+  continuum which, combined with SPHERE-IRDIS polarized images and a
+  well-sampled spectral energy distribution (SED), allow us to propose
+  a physical model for the source using radiative transfer (RT)
+  predictions.  The new ALMA data reveal a very thin ring at a radius
+  of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial
+  width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a
+  $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer
+  ring (Ring24) with a sharp inner edge at 24\,au. The steeply
+  decreasing brightness of Ring24 breaks at $\sim$35\,au into a
+  shallow tail. In order to reproduce the SED, the model that we
+  popose requires an inner ring at $\sim$6\,au (Ring6) in small dust
+  grains, hiding under the IRDIS coronagraph, and that surrounds an
+  inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02 $
+  ****GIVE ERRORS***) to the stellar position is picked up by ALMA.
+  The surprisingly thin Ring13 is nonetheless roughly 5 times wider
+  than the model scale height, and could thus be long-lived. The
+  strong near-far disc asymmetry at 1.65\,$\micron$ points at a very
+  forward-scattering phase function, and requires grain radii of no
+  less than 0.4\,$\micron$. The previously reported scattered-light
+  shadow of the secondary star is also reproduced by the RADMC3D RT
+  package. 
 \end{abstract}
@@
 
-Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
-The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
-%VLT/SPHERE 
-the current generation of high-contrast images 
-has mainly been towards the brighter sources \citep{Andrews2020arXiv200105007A}.
-The discs around T Tauri Stars (DARTTS) program was first presented in \citet{Avenhaus_2018} with the aim to image eight stars with the Spectro-Polarimeter High-contrast Exoplanet REsearch (SPHERE) \citep{2019A&A...631A.155B}.
-The sample is not biased towards exceptionally bright and large discs, and consists of only solar-type stars.
-A second part of the survey increased the number of sources by presenting 21 new images of circumstellar discs \citep{Garufi2020}.
-The observations revealed diverse structures and morphologies in the scattering surface of these discs.
-This letter on V4046 Sagittarii (Sgr) is part of the DARTTS survey with ALMA (DARTTS-A) which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
+Recent observations of young circumstellar discs have transformed
+current knowledge of planet formation. The focus of resolved imaging
+with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
+the current generation of high-contrast cameras has mainly been
+towards the brighter sources
+\citep[e.g.][]{Andrews2020arXiv200105007A} ***update to journal
+citation***. It is to address this bias that the programme called
+``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected
+differential polarization imaging (DPI) data secured with the
+Spectro-Polarimeter High-contrast Exoplanet REsearch
+\citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type
+stars \citep[][]{Avenhaus_2018,Garufi2020}. The sample is not biased
+towards exceptionally bright and large discs. The DARTTS observations
+revealed diverse structures and morphologies in the scattering surface
+of these discs. This letter on V4046 Sagittarii (Sgr) is part of a
+companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al. {\em in prep}), which
+will present millimetre observations of nine protoplanetary discs
+previously imaged in polarized scattered light in DARTTS-S.
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{refId0}.
-It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
-V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010}, with a rich observable chemical diversity \citep{Kastner_2018}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5
+and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and
+0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} ***DID ROSENFELD+
+PERFORM THESE MEASUREMENTS? IF NO USE CORRECT REFERENCE***, on a close
+($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital
+period of 2.42 days \citep{refId0}. It is a member of the $\beta$
+Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of
+23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is
+72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive
+($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au
+\citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
 
-The structure of this letter is as follows.
 The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}.
-We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}.
-Previous models of V4046\,Sgr have been made \citep{Ru_z_Rodr_guez_2019, Rosenfeld_2013, 2019ApJ...882..160Q} but our new ALMA data bring additional information.
+We interpret the data in terms of a parametric model, presented in Section~\ref{sec:model}, which builds up  on the previous models of V4046\,Sgr  \citep{Rosenfeld_2013, Ru_z_Rodr_guez_2019, 2019ApJ...882..160Q} to account for the new  ALMA data.
 Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.
@@
 Perez).
-These were acquired in the context of the DARTTS-A program (Perez et al.
-{\em in prep}), a larger survey for 9 optically visible TTauri discs at $\sim$50\,mas resolution.
-The survey simultaneously mapped the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with the C43-8 array configuration in band 6 (211-275\,GHz).
-This work focuses exclusively on the data obtained in the 1.3\,mm continuum for our source, acquired with baselines ranging from 92 to 8548\,m, which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$ (in natural weights).
+The observations  acquired simultaneously the 1.3\,mm continuum and the J = 2$-$1 line of $^{12}$CO with  (i.e.
+with a  band 6 211-275\,GHz correlator setup).
+The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$, in  natural weights.
+Here we focus on the continuum observations only.
 
-V4046 Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016.
-All the details of this observation can be found in the first DARTTS-S paper \citep{Avenhaus_2018} where the image was first published.
-Here we use a new reduction of the $H$ band data produced by the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
+V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
 The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}.
-The degree of linear polarization of the central and unresolved signal in V4046 Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
+The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
 The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
 
-For our analysis of the ALMA image we used an image reconstruction strategy, using the non-parametric image synthesis of the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C} it is possible to super-resolve the clean beam, obtaining an effective angular resolution $\sim$3 times finer than natural weights.
-The model image is obtained by fitting the data using Chi-squared minimisation, with a measure of regularization when required.
-Here we adopted a $\chi^2$ model image with $\lambda$ = 0.01 for regularization (***mem\_lS0.01\_lL0.0\_nogrid/mod\_out.fits**).
+Image synthesis of the ALMA continuum was performed with  the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C}, which fits a non-parametric model image $I^m_j$ to the data by comparing the  observed  and model visibilities, $V^\circ_k$ and $V^m_k$, using a least-squares figure of merit $L$:
+\begin{equation}
+  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
+\end{equation}
+The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
+\begin{equation}
+S = \sum_{j=1}^M \frac{I_j^m}{M} \ln\left(\frac{I_j^m}{M}\right),
+\end{equation}
+where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$).
+Here we set $\lambda = 0.01$.
+Similar applications of {\tt uvmem} in the context of protoplanetary disks can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.
+An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}.
+This angular resolution is comparable to  uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.
+
 The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
@@
 From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
 Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$).
+The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$) ***NOT THE SAME BEAM AS IN THE TEXT****, and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$) ***NOT 1/3 OF THE BEAM....
+NOT THE FIRST TIME THIS IS NOTICED, PLEASE FIX FOR GOOD****.
 The inset zooms into the central emission, and the green star marks the star positions.
-Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model.
-Bottom right panel: 1.3\,mm simulated image of the parametric model.
-The orange ellipse shows the size of the beam: $0\farcs035 \, \times \, 0\farcs031$.
+Bottom left panel: synthetic image at 1.65\,$\upmu m$.
+Bottom right panel: synthetic image at 1.3\,mm.
+.
 For all the images in the figure the colour scale is linear.}
@@
 
-Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position (at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}).
-We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 77.31$\pm$0.03\,$\degr$, an inclination of 32.96$\pm$0.02\,$\degr$ and a centre at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas, relative to the stars.
+Ring13 is surprisingly narrow and seems to be off-centred relative to the GAIA stellar position, at the origin of coordinates in Fig.~\ref{fig:images_vs_simulated}.
+We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles from 6\,au to 19\,au, by using the {\tt MPolarMaps} package described in Casassus et al.
+(2021, in prep).
+The resulting disk orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars.
+***PLEASE MAKE SURE THESE ARE THE FINAL AND CORRECT NUMBERS**** The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
+***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ****
 
@@
 After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.
+***MAKE SURE ALL NUMBERS ARE CONSISTENT****
 
-Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
-We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star.*** %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors,
-Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.
+In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars.
+We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors.
+However, perhaps due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation, as summarised in Fig.~\ref{fig:polarring}.
 
 Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}).
-Since this faint central emission is offset from the star, at the origin of coordinates in the figure, it is probably due to large dust grains.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system, and may be part of some inner structure possibly having to do with the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
-***
+Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
+This dust structure is at a distance of only $\sim0\farcs02$ from the binary system ****REPLACE WITH ESTIMATE OF THE RADIUS OF THIS CENTRAL BLOB, USE AN ELLIPTICAL GAUSSIAN FIT****, and may be part of inner disk introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+
 %match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
@@
 The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
-Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, described in detail by \citet{dOrazi}.
+Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
 
@@
 There is no hint of radio decrements in either Rings13 nor in Ring24 that would match shadowing at this PA.
-This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep{Casassus2019MNRAS.486L..58C}.
+This could be explained by inefficient disc cooling compared to the speed of the illumination pattern \citep[see ][ for estimates of this cooling timescale]{Casassus2019MNRAS.486L..58C}.
 
@@
 
-The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, online in \textsc{vizier}, and also using spectrometry data from an archival \textit{Spitzer} IRS spectrum (See Fig.~\ref{fig:SED}).
-The SED will provide us with missing information about the dust population.
+The observed SED was collected from data in the literature \citep{1988iras....7.....H, 1990A&A...234..230H, Jensen_97, 2000A&A...355L..27H, 2001KFNT...17..409K, 2003yCat.2246....0C, 2007PASJ...59S.369M, 2008PASP..120.1128O, 2010A&A...514A...1I, 2012yCat.2311....0C}, available online in \textsc{vizier}.
+We also  used  archival \textit{Spitzer} IRS spectroscopic data (see Fig.~\ref{fig:SED}).
 
@@
 Through trial and error, we found a set of values for the parameters that correctly fit the available data.
-The final structure of the parametric model goes as Fig.~\ref{fig:profiles} shows.
+The final structure of the parametric model is summarised in  Fig.~\ref{fig:profiles}.
 
-For the representation of the stars, we used two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C} with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
+For  stars were modeled using  two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
+We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
 
@@
 where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/2 for simplicity, as in \citet{Rosenfeld_2013}.
+For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/5 for simplicity ***(now is not for simplicity) OK SO EXPLAIN FURTHER *****.
 
@@
 Our model uses the same values, with two different flaring indexes $\psi$.
-The separation between the two values were set at $r$ = 19\,au with $\psi=0.2$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 1$\,au at $r_\circ = 19$\,au.
+The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
+The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.
 
-We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. Then it is defined by:
+We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
+The total gas surface density is then  given  by:
 \begin{equation}
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.6\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
 The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=6$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=1\times10^{13}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both structure components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both  components separately.
 
@@
 \end{equation}
-with $\delta_{\mathrm{sd}}$ = 5.2$\times 10^4$.
+with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.
 But the inner wall of Ring24 follows a different behaviour.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, marking the beginning and the maximum density peak of the outer ring respectively, the gas density profile is multiplied by an additional factor
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
 \begin{equation}
@@
 \end{equation}
-This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 19.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
-This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.6\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
+This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
 
@@
 The small dust grains are assumed to only make up for a fraction of $f_\mathrm{sd}=1\%$ of the total dust mass.
-As small dust is typically tightly coupled to the gas dynamics, its density profile is largely expected to follow the gas density.
+As small dust is typically tightly coupled to the gas dynamics, its density profile is  expected to follow the gas density.
 Then the density of small dust can be calculated as:
@@
 
-For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.36$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=4.2\times10^{13}$.
-For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, between 28.6 and 37\,au we chose a different value for $\gamma$ = -5 and $R_c$ = 38\,au.
-Thus, the surface density of the outer ring of large grains dust is defined by
+For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
+For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we chose different values for $\gamma$ = -5 and $R_c$ = 38\,au between 28.6 and 35.6\,au  ****THIS WOULD MEAN THAT YOU REVERT TO THE OTHER VALUES OUTSIDE THIS RANGE, ALSO OUTSIDE 35.6AU - IS THAT WHAT YOU MEANT?****.
+The surface density of the outer ring of large grains dust is thus given by
 \begin{equation}
@@
   0                 & r < 24.6\text{\,au} \\
-  4.37 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
-  2.04 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  1.82 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
+  2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
+  2.14 \times10^{5} & 37   < r < 64\text{\,au.} \\
   \end{cases}
@@
 The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
-We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 70\% silicate and 30\% graphite.
+We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
 
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$, and smeared out by 30\% in both directions, and using 20 grain size bins within that range.
-This distribution applies only to generate the NIR image.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$ but  smeared out by 30\%, and with 20 grain size bins within that range.
+This distribution applies only to generate the NIR $Q_\phi$ image.
+****YOU SHOULD EXPLAIN HERE HOW YOU CALCULATED THE QPHI IMAGES - YOU CAN USE THE MATERIAL IN THE DOAR44 PAPER***
 
@@
 
-The inner radius of the model grid was set to 0.1\,au and an outer radius of 100\,au, large enough for the dust disc to become undetectable.
-We set the values of the inclination an the position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+The inner radius of the model grid was set to 0.1\,au,  and the outer radius of 100\,au, which is large enough for the dust disc to become undetectable.
+We set the values of the inclination an disk  position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
 = 77.31\,$\degr$.
@@
 The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
-The visible asymmetry in the SPHERE observations is recreated using grains larger than 0.4\,$\micron$ as smaller grains do not cause a strong forward scattering, meaning that the disc is depleted of very-small grains.
+The visible asymmetry in the SPHERE observations is reproduced using relative large grains,  $\sim$0.4\,$\micron$, as smaller grains did not result in such  strong forward scattering.
+This suggests tha the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
+*****POINT HERE TO A DISCUSSION OF THE FORWARD SCATTERING PHASE FUNCTION AND ITS EFFECT DESCRIBED IN THE STOLKER PAPER *****
 
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
-As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a good approximation of the disc structure, including the dimensions of Ring13.
+As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
 Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
-The total dust mass of Ring13 is about 1.5\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$49\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.04\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
-%As \citet{2018ApJ...869L..46D} explain the stability of a narrow dust ring requires that its height is smaller than its radial extent. 
-Using the large grains scale height of 0.66\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$2.3 times more extended in radial than in vertical direction.
+The total dust mass of Ring13 is about 1.1\,M$_{\earth}$ in the model.
+In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$50\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
+Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended  radially than vertically.
 
-The observed structure may point to the existence of planet-disk interaction within this system, where a giant planet depletes its orbit of gas and dust material.
+The observed structure may point to the existence of planet-disk interactions within this system, where a giant planet depletes its orbit of gas and dust material.
 A possible  constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
 As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
-This idea is supported by the similarity to the structure around HD 169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
-%We point out that also the disk dispersal by photoevaporative winds \citep{1994ApJ...428..654H} as causation of the inner cavity cannot be ruled out at his stage.
+This idea is supported by the similarity to the structure around HD\,169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
+****IS THIS THE APPROPIATE CITATION?
+PROBABLY ASK PHILIPP***
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
-The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
+*** The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
+%The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
 Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
 Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 4.83\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+****FINISH THIS PARA****
 
@@
 \end{equation}
-where we implicitly assumed the turbulent diffusivity to be equal to the turbulent viscosity.
-Here, $\alpha$ represents the typical parameter for turbulent viscosity, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observed fluxes corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$, yields $\mathrm{St}\approx 0.03$.
+where we  assumed the turbulent diffusivity to be equal to the turbulent viscosity $\alpha$, and $\mathrm{St}$ is the dimensionless Stokes number.
+Assuming that the most relevant grain size for observations at a wavelength $\lambda$ corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$ ***not up to date FIX THEN ****, yields $\mathrm{St}\approx 0.03$.
 With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity.
@@
 %and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
-Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would have to have millimetre-size dust grains due to dust trapping, and those grains are not present in the ALMA observation.
-***
+Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would trap  millimetre-size dust grains , while  those grains are not present in the ALMA observation.
+***  ***PERHAPS TOO FAINT?
+HOW DOES THE MASS OF RING6 COMPARE WITH THE INNER DISK?****
 
@@
   \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.5\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.66\,au at 13.32\,au) we have that the ring width is roughly 2.3 times its estimated height.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.1\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.31\,au at 13.32\,au) we have that the ring width is roughly 4.8 times its estimated height.
 
@@
   \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars.
+
   %We also predict the existence of another thin ring at $\sim$6\,au, about 3\,au-wide and made of small dust grains, and that lies under the coronagraph of the scattered-light image. 

### 2020-12-08 Draft_V4046Sgr_mnras.tex
SC edits

@@
 \begin{abstract}
-  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc
-  known for its wide cavity and dusty ring.  We present high
-  resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm
-  continuum which, combined with SPHERE-IRDIS polarized images and a
-  well-sampled spectral energy distribution (SED), allow us to propose
-  a physical model for the source using radiative transfer (RT)
-  predictions.  The new ALMA data reveal a very thin ring at a radius
-  of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial
-  width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a
-  $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer
-  ring (Ring24) with a sharp inner edge at 24\,au. The steeply
-  decreasing brightness of Ring24 breaks at $\sim$35\,au into a
-  shallow tail. In order to reproduce the SED, the model that we
-  popose requires an inner ring at $\sim$6\,au (Ring6) in small dust
-  grains, hiding under the IRDIS coronagraph, and that surrounds an
-  inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02 $
-  ****GIVE ERRORS***) to the stellar position is picked up by ALMA.
-  The surprisingly thin Ring13 is nonetheless roughly 5 times wider
-  than the model scale height, and could thus be long-lived. The
-  strong near-far disc asymmetry at 1.65\,$\micron$ points at a very
-  forward-scattering phase function, and requires grain radii of no
-  less than 0.4\,$\micron$. The previously reported scattered-light
-  shadow of the secondary star is also reproduced by the RADMC3D RT
-  package. 
+  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
+We present high resolution ($\sim$20--50\,mas **** WRONG UPDATE TO CORRECT NUMBERS****) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
+The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
+Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
+The intensity plateau in Ring24 breaks at $\sim$35\,au, where it steeply drops  and  extends into  a shallow tail.
+A compact source of mm-continuum at  the stellar position is picked up by ALMA, with a radius of ***RADIUS OF THE BLOB, IS IT RESOLVED?***.
+In order to reproduce the SED in the IR, our RT model  requires an  inner circumbinary disc ***GIVE RADII*** rich in small grains (as in previous  models of V4046\,Sgr), and  which  matches the  central ALMA signal if it contains **Xxx*** Mearths in large dust.
+An inner  ring at $\sim$6\,au (Ring6) composed of small  grains, with a gas mass of ***Mearth*** and deprived of large dust, is required to explain the ***10$\mu$m ???*** flux density.
+The surprisingly thin Ring13 is nonetheless $\sim$5 times wider ****NOT CONSISTENT WITH CONCLUSIONS*** in the ALMA signal  than the model scale height, and $\sim$3***???*** narrower than the model gas radial width.
+Ring13 could thus be   long-lived and shaped by radial dust trapping, which would require a turbulence value of  $\alpha_{\rm turb} \sim 0.01$.
+The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
+The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package.
 \end{abstract}
@@
 
-Recent observations of young circumstellar discs have transformed
-current knowledge of planet formation. The focus of resolved imaging
-with the Atacama Large Millimetre/submillimetre Array (ALMA) or with
-the current generation of high-contrast cameras has mainly been
-towards the brighter sources
-\citep[e.g.][]{Andrews2020arXiv200105007A} ***update to journal
-citation***. It is to address this bias that the programme called
-``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected
-differential polarization imaging (DPI) data secured with the
-Spectro-Polarimeter High-contrast Exoplanet REsearch
-\citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type
-stars \citep[][]{Avenhaus_2018,Garufi2020}. The sample is not biased
-towards exceptionally bright and large discs. The DARTTS observations
-revealed diverse structures and morphologies in the scattering surface
-of these discs. This letter on V4046 Sagittarii (Sgr) is part of a
-companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al. {\em in prep}), which
-will present millimetre observations of nine protoplanetary discs
-previously imaged in polarized scattered light in DARTTS-S.
+Recent observations of young circumstellar discs have transformed current knowledge of planet formation.
+The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}.
+It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}.
+The sample is not biased towards exceptionally bright and large discs.
+The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs.
+This letter on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al.
+{\em in prep}), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.
 
-V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5
-and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and
-0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012} ***DID ROSENFELD+
-PERFORM THESE MEASUREMENTS? IF NO USE CORRECT REFERENCE***, on a close
-($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital
-period of 2.42 days \citep{refId0}. It is a member of the $\beta$
-Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of
-23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is
-72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive
-($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au
-\citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
+V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}.
+It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
+V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
 
@@
 with a  band 6 211-275\,GHz correlator setup).
-The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs077 \,\times \, 0\farcs051$, in  natural weights.
+The ALMA array was in its C43-8 configuration, with baselines ranging from 92 to 8548\,m which translate into a synthesized beam of $0\farcs062 \,\times \, 0\farcs055$, in  natural weights.
 Here we focus on the continuum observations only.
 
-V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
+V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE-IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}.
 Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization.
@@
 The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures.
-The angle of polarization is aligned with the disk major disk, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
+The angle of polarization is aligned with the disc major axis, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.
 
@@
 \begin{equation}
-  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
+  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 - \lambda S.
 \end{equation}
@@
 Here we set $\lambda = 0.01$.
-Similar applications of {\tt uvmem} in the context of protoplanetary disks can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.
+Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.
 An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}.
@@
 
-The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
+The resulting {\tt uvmem} image shown in the top right panel of Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc.
 This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e.
@@
   \includegraphics[width=\textwidth]{hot_two_E.pdf}
-  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr.
-From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.
-Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
-Top right panel: 1.3\,mm continuum {\tt uvmem} model image.
-The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$) ***NOT THE SAME BEAM AS IN THE TEXT****, and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$) ***NOT 1/3 OF THE BEAM....
-NOT THE FIRST TIME THIS IS NOTICED, PLEASE FIX FOR GOOD****.
-The inset zooms into the central emission, and the green star marks the star positions.
-Bottom left panel: synthetic image at 1.65\,$\upmu m$.
-Bottom right panel: synthetic image at 1.3\,mm.
+  \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
+\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+\textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
+***NO YELLOW ELLIPSE?*** The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$ **WRONG***).
+The inset zooms into the central emission, and the green star marks the binary position.
+\textit{Bottom left panel:} synthetic image at 1.65\,$\micron$.
+\textit{Bottom right panel:} synthetic image at 1.3\,mm.
 .
@@
 (2021, in prep).
-The resulting disk orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars.
-***PLEASE MAKE SURE THESE ARE THE FINAL AND CORRECT NUMBERS**** The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
-***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ****
+The resulting disc orientation is set at a position angle  (PA) of 77.31$\pm$0.03\,$\degr$, with an  inclination of 32.96$\pm$0.02\,$\degr$, and the optimal ring  centre is at $\Delta \alpha = -4\pm0.02$\,mas $\Delta \delta = 13\pm0.05$\,mas relative to the GAIA position of the stars.
+The offset of the center of the cavity and the nominal stellar positions is entirely consistent with a pointing error, since the pointing accuracy of ALMA is usually taken to be 1/10 of the natural-weights beam, at 1\,$\sigma$, or $\sim$6\,mas in this case.
+***ANTONIO PLEASE CONFIRM AND PROVIDE A REFERENCE ***
 
@@
 After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.
-***MAKE SURE ALL NUMBERS ARE CONSISTENT****
 
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
-This dust structure is at a distance of only $\sim0\farcs02$ from the binary system ****REPLACE WITH ESTIMATE OF THE RADIUS OF THIS CENTRAL BLOB, USE AN ELLIPTICAL GAUSSIAN FIT****, and may be part of inner disk introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
+The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
 
@@
 
-The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
+The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution.
 The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au.
@@
 
-For  stars were modeled using  two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
+The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}.
 The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.
@@
 Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging.
-We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.
+We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach higher regions above the mid-plane.
 
@@
 \end{equation}
-where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
-For the gas and the small dust grains $\chi$ = 1 and for the millimetre-size dust population we assign a fixed $\chi$ = 1/5 for simplicity ***(now is not for simplicity) OK SO EXPLAIN FURTHER *****.
+where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling.
+The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1.
+The radial spread of Ring13 appears about three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{\mathrm{ld}}=0.3$.
 
 For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one.
-Our model uses the same values, with two different flaring indexes $\psi$.
-The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24.
-The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.
+Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$.
+The separation between the two values were set at $r = 18$\,au with $\psi_1=0.15$ for Ring6 and Ring13, and $\psi_2=0.5$ for Ring24.
+The scale height is $H_\circ = 0.67$\,au at $r_\circ = 18$\,au.
 
-We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
-The total gas surface density is then  given  by:
+We propose a three ringed structure to reproduce the observations.
+We separate the disk into four individual regions: the inner disc, Ring6, Ring13 and Ring24.
+The combined gas surface density profile is then given by:
 \begin{equation}
@@
 
-The inner disk follows a power law function defined by
+The inner disc follows a power law function defined by
 \begin{equation}
@@
 \end{equation}
-where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
-The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.
+where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.8\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}
 
-We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
+We choose to use Gaussian profiles to parameterize Ring6 and Ring13,
 \begin{equation}
@@
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both  components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
 
-For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
+For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.9$\times 10^4$:
 \begin{equation}
@@
 \end{equation}
-with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.
-But the inner wall of Ring24 follows a different behaviour.
-Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
+The inner edge of Ring24 follows a different profile.
+Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
 \begin{equation}
@@
 \end{equation}
-This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
+This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
 This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
@@
 Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
-We also truncated the model large-grain density at 64\,au.
-The large-dust surface density profile is defined by the sum of its two components
+We also truncated the profile of large dust grains at 64\,au.
+It is then defined by the sum of its two components
 \begin{equation}
@@
 
-For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$.
-For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we chose different values for $\gamma$ = -5 and $R_c$ = 38\,au between 28.6 and 35.6\,au  ****THIS WOULD MEAN THAT YOU REVERT TO THE OTHER VALUES OUTSIDE THIS RANGE, ALSO OUTSIDE 35.6AU - IS THAT WHAT YOU MEANT?****.
-The surface density of the outer ring of large grains dust is thus given by
+For the inner ring, we choose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3.27\times10^{13}$.
+For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -4$ and $R_c$ = 39\,au between 28.6 and 35.6\,au.
+The surface density for large dust grains in the outer ring is thus given by
 \begin{equation}
@@
   \begin{cases}
-  0                 & r < 24.6\text{\,au} \\
-  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
-  2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
-  2.14 \times10^{5} & 37   < r < 64\text{\,au.} \\
+  0                 & r < 24.7\text{\,au} \\
+  6.13 \times10^{4} & 24.7 < r < 28.6\text{\,au} \\
+  2.34 \times10^{4} & 28.6 < r < 35.6\text{\,au} \\
+  2.10 \times10^{5} & 35.6 < r < 64\text{\,au.} \\
   \end{cases}
@@
 The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package.
-As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$ but  smeared out by 30\%, and with 20 grain size bins within that range.
+As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we centred a Gaussian at 0.4\,$\micron$, smeared out by 30\%, and with distributed over 20 bins within that range.
 This distribution applies only to generate the NIR $Q_\phi$ image.
-****YOU SHOULD EXPLAIN HERE HOW YOU CALCULATED THE QPHI IMAGES - YOU CAN USE THE MATERIAL IN THE DOAR44 PAPER***
+To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.
 
@@
 	\includegraphics[width=\columnwidth]{allprofiles.png}
-        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations.
+        \caption{{\bf Top:} surface density profiles for gas, large and small dust grains.
 {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
-The dashed lines crossing both panels correspond to transition radii in the parametric model.}
+The dotted lines crossing both panels correspond to transition radii in the parametric model.}
     \label{fig:profiles}
@@
 
-The inner radius of the model grid was set to 0.1\,au,  and the outer radius of 100\,au, which is large enough for the dust disc to become undetectable.
-We set the values of the inclination an disk  position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A.
+The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable.
+We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,$\degr$ and a P.A.
 = 77.31\,$\degr$.
-Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.
+Finally, the distance is set to d = 72.4\,pc \citep{Gaia}.
 
@@
 The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
-The visible asymmetry in the SPHERE observations is reproduced using relative large grains,  $\sim$0.4\,$\micron$, as smaller grains did not result in such  strong forward scattering.
-This suggests tha the disc is depleted of very-small grains.
+The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
+As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are relatively large, suggesting that the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
-*****POINT HERE TO A DISCUSSION OF THE FORWARD SCATTERING PHASE FUNCTION AND ITS EFFECT DESCRIBED IN THE STOLKER PAPER *****
 
@@
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13 we have that it has a radius of 13.36\,au, a FWHM of 1.30\,au, and a scale height FWHM of the millimetre-size dust of 0.65\,au.
-The total dust mass of Ring13 is about 1.1\,M$_{\earth}$ in the model.
-In turn, in our model Ring24 reaches peak intensity at $\sim$30\,au, then breaks at $\sim$36\,au, as in the observations, and has a total dust mass of $\sim$50\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.2\,au difference in the width estimation.
-Using the large grains scale height of 0.31\,au at Ring13, and a measured width of 1.50\,au, the ring is $\sim$4.8 times more extended  radially than vertically.
+Accordingly, taking the parametric model values for Ring13, it has a radius of 13.38\,au, a FWHM of 1.27\,au, and a scale height FWHM of the millimetre-size dust of 0.48\,au.
+The total dust mass of Ring13 is about 0.9\,M$_{\earth}$ in the model.
+In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au.
+It contains a total dust mass of $\sim$35\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.23\,au difference in the width estimation.
+Using the large grain scale height at Ring13 of 0.48\,au, and a measured width of 1.50\,au, the ring is $\sim$3.1 times more extended radially than vertically.
 
-The observed structure may point to the existence of planet-disk interactions within this system, where a giant planet depletes its orbit of gas and dust material.
-A possible  constellation in this scenario is therefore the presence of two giant planets in the disk, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
+The observed structure may point to the existence of planet-disc interactions within this system, where a giant planet depletes its orbit of gas and dust material.
+A possible  constellation in this scenario is therefore the presence of two giant planets in the disc, one planet between the star and Ring13, and one planet between Ring13 and Ring24.
 As \citet{Ru_z_Rodr_guez_2019} suggest, the putative planet between Ring13 and Ring24 may be a giant planet with a mass within the range of 0.3$-$1.5\,$\mathrm{M}_{\mathrm{Jup}}$.
-This idea is supported by the similarity to the structure around HD\,169142 which \citet{bertrang_avenhaus_2018} reproduced by including several giant planets.
-****IS THIS THE APPROPIATE CITATION?
-PROBABLY ASK PHILIPP***
+This idea is supported by the similarity to the structure around HD\,169142 which \citet{2020arXiv200711565B} reproduced by including several giant planets.
 
-*** The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
-%The most suitable RT model demands a density distribution of small grains and gas that is radially more extended, with an approximate width of $7.5\mathrm{au}$.
-Although the RT model ascribed step functions to gas and dust densities, in a more physical scenario the density should roughly follow a Gaussian distribution.
-Using that the gas' Ring13-FWHM in the RT model corresponds to $w_\mathrm{g} = 4.83\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
-****FINISH THIS PARA****
+The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
+Using that the FWHM of Ring13 in the   RT model for the gas  corresponds to $w_\mathrm{g} = 5.32\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
 
-Similarly to \citet{2018ApJ...869L..46D}, the ratio between dust and gas ring width can be linked to important properties:
-\begin{equation}\label{eq:ringwidth}
-        \frac{w_\mathrm{d}}{w_\mathrm{g}} = \sqrt{\frac{\alpha}{\alpha+\mathrm{St}}}\,,
-\end{equation}
-where we  assumed the turbulent diffusivity to be equal to the turbulent viscosity $\alpha$, and $\mathrm{St}$ is the dimensionless Stokes number.
-Assuming that the most relevant grain size for observations at a wavelength $\lambda$ corresponds to $a = \lambda_{\mathrm{obs}}/(2 \pi)$, and estimating the gas surface density within Ring13 from the RT model to be roughly $20\,\mathrm{g}/\mathrm{cm}^2$ ***not up to date FIX THEN ****, yields $\mathrm{St}\approx 0.03$.
-With these considerations, equation~\ref{eq:ringwidth} provides a value of $\alpha \approx 0.001$ for the level of turbulent viscosity.
-We emphasise that this relies on rough estimates and is additionally restricted to the area within Ring13.
-Yet, its moderate value agrees with the limit \citet{2018ApJ...869L..46D} inferred from multiple dust rings at larger orbital distances ($\alpha \gtrsim 5\times10^{-4}$).
-Further, it is also consistent with the non-detection of non-thermal broadening of CO lines reported by \citet{Flaherty_2020}, from which the authors deduced an upper limit of $\alpha \lesssim 10^{-3}$ at the midplane of V4046\,Sgr.
+Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of considerable turbulent diffusion.
+Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St ****GIVE FORMULA USED HERE****, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$.
+The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
+With these values, the relevant Stokes number is approximated to be St$\approx 0.1$.
+This yields an estimate for the level of diffusivity of $D\approx 0.01$.
+It further provides a value for the level of turbulence in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming turbulence to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+We note that the obtained value for $\alpha_{\rm turb}$ is larger than typical expectations \citep[e.g.][for V4046 Sgr]{Flaherty_2020} *****QUOTE THE EXPECTATIOMS???i think that theirs is an upper limit****.
+Our estimate  carries uncertainties originating from estimates of the local gas density, which varies proportionally to the dust-to-gas mass ratio $\zeta$,
+
+**** as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains in the observations <<< I WOULD REMOVE THIS.
 
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
-The decision of employing the three ringed structure for the small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$.
-%and we may have detected this ring in the ALMA image, if this ring is lopsided or shadowed by the secondary. 
-Ring6 may be just artificial and not a real prediction, as a thin ring like the one needed would trap  millimetre-size dust grains , while  those grains are not present in the ALMA observation.
-***  ***PERHAPS TOO FAINT?
-HOW DOES THE MASS OF RING6 COMPARE WITH THE INNER DISK?****
+From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au ****SO IN LINE WITH PREVIOUS RT MODELS, CITE THEM***.
+The decision of employing a three ringed structure for the gas and  small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$, which we place here at 6\,au (Ring6).
+This ring  is intriguing  as it is deprived of millimetre-size dust grains to explain its absence in the ALMA image (***upper limit Zeta in this ring??
+use 3 times noise value in the ALMA image***), while  a thin ring like the one we implemented would be expected to trap millimetre-size dust grains.
 
@@
 \begin{enumerate}
-  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.32$\pm$0.26\,au and an estimated width of 1.50$\pm$0.72\,au.
-The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 1.1\,M$_{\earth}$ millimetre-sized grains.
-Using the parametric model scale height value ($H= $ 0.31\,au at 13.32\,au) we have that the ring width is roughly 4.8 times its estimated height.
+\item We report the detection of a radio counterpart to the inner ring observed in  scattered-light images.
+This ring is much narrower  in the 1.3\,mm continuum, with a radial width of 1.50$\pm$0.72\,au at a radius of 13.32$\pm$0.26\,au.
+According to our RT model, this ring contains 0.9\,M$_{\earth}$ in millimetre-sized grains.
+Its width in the dust is still 3.1 times its estimated height  ($H= $ 0.48\,au at 13.32\,au), and **** times narrower than the gas, which make it a case of strong radial trapping in a long-lived ring.
 
-  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$35\,au.
+  \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
+***HOW IS THIS BREAK INTERPRETED IN THE RT**** ??
 
@@
   \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars.
+***IN LINE WITH PREVIOUS WORK**** except for ring6, comment on this and explain it.
 
@@
 
-\section*{Data Availability}
+%\section*{Data Availability}
 

### 2021-01-20 Draft_V4046Sgr_mnras.tex
SC edits

@@
   The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.
-We present high resolution ($\sim$20--50\,mas **** WRONG UPDATE TO CORRECT NUMBERS****) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
-The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au.
+We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions.
+The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au.
 Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au.
-The intensity plateau in Ring24 breaks at $\sim$35\,au, where it steeply drops  and  extends into  a shallow tail.
-A compact source of mm-continuum at  the stellar position is picked up by ALMA, with a radius of ***RADIUS OF THE BLOB, IS IT RESOLVED?***.
-In order to reproduce the SED in the IR, our RT model  requires an  inner circumbinary disc ***GIVE RADII*** rich in small grains (as in previous  models of V4046\,Sgr), and  which  matches the  central ALMA signal if it contains **Xxx*** Mearths in large dust.
-An inner  ring at $\sim$6\,au (Ring6) composed of small  grains, with a gas mass of ***Mearth*** and deprived of large dust, is required to explain the ***10$\mu$m ???*** flux density.
-The surprisingly thin Ring13 is nonetheless $\sim$5 times wider ****NOT CONSISTENT WITH CONCLUSIONS*** in the ALMA signal  than the model scale height, and $\sim$3***???*** narrower than the model gas radial width.
-Ring13 could thus be   long-lived and shaped by radial dust trapping, which would require a turbulence value of  $\alpha_{\rm turb} \sim 0.01$.
+The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail.
+In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc.
+The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height, and could thus be long-lived.
 The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$.
@@
 V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}.
-It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}.
+It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}.
 V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.
@@
 \begin{equation}
-  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 - \lambda S.
+  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
 \end{equation}
@@
   \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr.
-\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc.
+\textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 71.48\,pc.
 \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image.
-***NO YELLOW ELLIPSE?*** The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$ **WRONG***).
+The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs021 \, \times \, \sim0\farcs018$).
 The inset zooms into the central emission, and the green star marks the binary position.
@@
 The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth.
-On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
+On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au (See Fig.~\ref{fig:polarring}).
 As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved.
-After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.
+After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs021 \,\times \,\sim0\farcs018$), the ring width is $\sim$2.46$\pm$0.56\,au.
 
@@
 Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars.
-The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
-
-%match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below).
-If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.
+The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au.
+If this feature is caused by the presence of millimeter-size dust, its estimated mass would be around 0.12\,M$_{\earth}$.
+%and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).
 
@@
 The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}.
-Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
+Two other important features that are present in the image are: the brightness asymmetry, and the shadows projected on the disc by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.
 
@@
 The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1.
-The radial spread of Ring13 appears about three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
-We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{\mathrm{ld}}=0.3$.
+The radial spread of Ring13 appears two to three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA.
+We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disc's midplane), leading to $\chi_{\mathrm{ld}}=0.4$.
 
@@
 Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$.
-The separation between the two values were set at $r = 18$\,au with $\psi_1=0.15$ for Ring6 and Ring13, and $\psi_2=0.5$ for Ring24.
-The scale height is $H_\circ = 0.67$\,au at $r_\circ = 18$\,au.
+The separation between the two values were set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24.
+The scale height is $H_\circ = 0.88$\,au at $r_\circ = 18$\,au.
 
 We propose a three ringed structure to reproduce the observations.
-We separate the disk into four individual regions: the inner disc, Ring6, Ring13 and Ring24.
+We separate the disc into four individual regions: the inner disc, Ring5, Ring13 and Ring24.
 The combined gas surface density profile is then given by:
 \begin{equation}
-  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
+  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
 \end{equation}
@@
 where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index.
-We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.8\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
+We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.26\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.
 Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}
 
-We choose to use Gaussian profiles to parameterize Ring6 and Ring13,
+We choose to use Gaussian profiles to parameterize Ring5 and Ring13,
 \begin{equation}
-  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
+  \Sigma_{\mathrm{ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
   \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
 \end{equation}
-where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
+where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.3$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.28$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6 \times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.
 
-For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.9$\times 10^4$:
+For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.2$\times 10^4$:
 \begin{equation}
-  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
+  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
 \end{equation}
@@
 \end{equation}
-This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.8\,au.
-This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
+This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.
+This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.
 
@@
 
-Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring.
-We also truncated the profile of large dust grains at 64\,au.
-It is then defined by the sum of its two components
+Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring.
+To be consistent with the theory, Ring5 should have a small large-dust population too, but, as this ring is not visible in the ALMA observation, we added just the right mass to be undetectable by the ALMA observation.
+We also truncated the profile of large dust grains at 63\,au.
+It is then defined by the sum of its three components
 \begin{equation}
-  \Sigma_{\mathrm{ld}}(r) = 
+  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
   \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
@@
 
-For the inner ring, we choose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3.27\times10^{13}$.
-For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -4$ and $R_c$ = 39\,au between 28.6 and 35.6\,au.
+For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.34\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.41\,\mathrm{au\,g\,cm^{-3}}$.
+For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au.
 The surface density for large dust grains in the outer ring is thus given by
 \begin{equation}
-    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
+    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
 \end{equation}
@@
   \begin{cases}
-  0                 & r < 24.7\text{\,au} \\
-  6.13 \times10^{4} & 24.7 < r < 28.6\text{\,au} \\
-  2.34 \times10^{4} & 28.6 < r < 35.6\text{\,au} \\
-  2.10 \times10^{5} & 35.6 < r < 64\text{\,au.} \\
+  0                 & r < 24.6\text{\,au} \\
+  7.19 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
+  3.17 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
+  2.65 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
   \end{cases}
@@
 \begin{equation}
-\rho_{\mathrm{large-dust}}(r,z)=
+\rho_{\mathrm{large\,dust}}(r,z)=
 \frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
@@
 
-The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm.
+The two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm.
 We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.
@@
 {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$.
+The dashed brown line indicates the undetectable large grains in Ring5.
 The dotted lines crossing both panels correspond to transition radii in the parametric model.}
@@
 = 77.31\,$\degr$.
-Finally, the distance is set to d = 72.4\,pc \citep{Gaia}.
+Finally, the distance is set to d = 71.48\,pc \citep{gaiacollaboration2020gaia}.
 
@@
 
-The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph.
+The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring5 hides under the artificial coronagraph.
 The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering.
-As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are relatively large, suggesting that the disc is depleted of very-small grains.
+As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very-small grains.
 Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.
@@
     \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images.
-The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
+The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
     \label{fig:radprofiles}
@@
 The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24.
+The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$).
+This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim2\times10^{-5}$\,M$_{\earth}$.
+
 As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13.
-Accordingly, taking the parametric model values for Ring13, it has a radius of 13.38\,au, a FWHM of 1.27\,au, and a scale height FWHM of the millimetre-size dust of 0.48\,au.
-The total dust mass of Ring13 is about 0.9\,M$_{\earth}$ in the model.
+Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-size dust of 0.61\,au.
+The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model.
 In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au.
-It contains a total dust mass of $\sim$35\,M$_{\earth}$.
-The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.06\,au difference in the centroid location of the ring, and a 0.23\,au difference in the width estimation.
-Using the large grain scale height at Ring13 of 0.48\,au, and a measured width of 1.50\,au, the ring is $\sim$3.1 times more extended radially than vertically.
+It contains a total dust mass of $\sim$44\,M$_{\earth}$.
+The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation.
+Since  the  scale height of the large grains in Ring13 is  0.61\,au, and has a  measured width of 2.46\,au ***if you say measured you should give errors ***, the ring is $\sim$4.1***+-?*** times more extended radially than vertically.
 
@@
 
-The effective beam size of the presented ALMA observations marginally resolves the width of Ring13 to be $w_\mathrm{d} = 1.50\mathrm{au}$.
-Using that the FWHM of Ring13 in the   RT model for the gas  corresponds to $w_\mathrm{g} = 5.32\mathrm{au}$, we can see that large dust grains have to be radially converged to explain the discrepancy.
+The effective beam size of these new  ALMA observations marginally resolves  Ring13, with a width of  $w_\mathrm{d} = 2.46\mathrm{au}$.
+Using that the FWHM of Ring13 in the gas is $w_\mathrm{g} = 5.42\mathrm{au}$ from the RT model, we can see that large dust grains have to be radially converged.
+****is $w_\mathrm{d}$ also a FWHM??****
 
 Even though the radial spread of large dust grains in Ring13 appears to be quite thin, the width in comparison to the sub-lying gas profile speaks for the presence of considerable turbulent diffusion.
-Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St ****GIVE FORMULA USED HERE****, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$.
-The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$, the RT model prescribes a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
+Following a similar ring analysis as in \citet{2018ApJ...869L..46D}, we find that the ratio between the dimensionless diffusion parameter, $D$, and the dimensionless Stokes number, St, (which parameterizes the dynamical behaviour of a grain) is roughly, $D/{\rm St}\approx 0.1$.
+The observed signal is expected to be dominated by grains of size $a\approx 0.02\,{\rm cm}$.
+The RT model, together with the dust-to-gas ratio of 0.05, prescribe a gas density of $\Sigma_{\rm g} \approx 0.5\,{\rm g}{\rm cm}^{-2}$ to the location of Ring13.
 With these values, the relevant Stokes number is approximated to be St$\approx 0.1$.
 This yields an estimate for the level of diffusivity of $D\approx 0.01$.
-It further provides a value for the level of turbulence in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming turbulence to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
-We note that the obtained value for $\alpha_{\rm turb}$ is larger than typical expectations \citep[e.g.][for V4046 Sgr]{Flaherty_2020} *****QUOTE THE EXPECTATIOMS???i think that theirs is an upper limit****.
-Our estimate  carries uncertainties originating from estimates of the local gas density, which varies proportionally to the dust-to-gas mass ratio $\zeta$,
-
-**** as well as the fact that the width of Ring13 is measured at different vertical positions for small and large grains in the observations <<< I WOULD REMOVE THIS.
+It further provides a value for the level of turbulent viscosity in Ring13, $\alpha_{\rm turb}\approx 0.01$, assuming viscosity to be equal to the level of diffusion \citep{2007Icar..192..588Y}.
+We note that an observation of molecular line broadening has found no evidence for turbulent contributions, suggesting $\alpha_{\rm turb}<0.01$ (Flaherty et al.
+2020 *****REFERENCE****).
+The value inferred from our model is just within this limit.
+It is linearly proportional to the local dust-to-gas ratio (by our definition of the gas surface density profile) -- a standard ISM  value of 0.01 for the dust-to-gas ratio would thus lead to an expected level of turbulent viscosity of $\alpha_{\rm turb}\approx 5\times10^{-3}$.
+While the exact value for $\alpha_{\rm turb}$ is not well constrained, the presence of turbulence is a robust detection, as it is required to explain the radial spread of the resolved Ring13.
 
 The observed SED is compared with the model in Fig.~\ref{fig:SED}.
-From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au ****SO IN LINE WITH PREVIOUS RT MODELS, CITE THEM***.
-The decision of employing a three ringed structure for the gas and  small dust grains relies on the fact that the SED needed a ring at a radius smaller than 10\,au to have a proper fit around 10\,$\micron$, which we place here at 6\,au (Ring6).
-This ring  is intriguing  as it is deprived of millimetre-size dust grains to explain its absence in the ALMA image (***upper limit Zeta in this ring??
-use 3 times noise value in the ALMA image***), while  a thin ring like the one we implemented would be expected to trap millimetre-size dust grains.
+From the similarity with the data we propose that there has to be a small-grain population close to the stars down to 0.3\,au.
+The observed central and compact signal  in the ALMA observation cannot be explained using  millimeter-sized dust, following the mass estimates in Section\,\ref{sec:Observations}, as ****it reaches xxx times large surface densities than in the gas?***.
+Also, the hypothesis of thermal emission from large grain in the inner disk results in  a large excess at 10$\,\micron$ that does not match the data.
+The decision of employing the three ringed structure (i.e.
+add Ring5 to the observed structure) relies on the fact that the SED needed a ring at a radius around 5--7\,au to have a proper fit around 10\,$\micron$.
+
+%Ring5 may be just artificial and not a real prediction, as a thin ring like the one we implemented would be expected to trap millimetre-size dust grains, while those grains are not present in the ALMA observation.
 
@@
 \begin{enumerate}
-\item We report the detection of a radio counterpart to the inner ring observed in  scattered-light images.
-This ring is much narrower  in the 1.3\,mm continuum, with a radial width of 1.50$\pm$0.72\,au at a radius of 13.32$\pm$0.26\,au.
-According to our RT model, this ring contains 0.9\,M$_{\earth}$ in millimetre-sized grains.
-Its width in the dust is still 3.1 times its estimated height  ($H= $ 0.48\,au at 13.32\,au), and **** times narrower than the gas, which make it a case of strong radial trapping in a long-lived ring.
+  \item We report the detection of a narrow ring in the 1.3\,mm continuum, with a radius 13.15$\pm$0.26\,au and an estimated width of 2.46$\pm$0.56\,au.
+The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes around 0.7\,M$_{\earth}$ millimetre-sized grains.
+Using the parametric model scale height value ($H= $ 0.60\,au at 13.15\,au) we have that the ring width is roughly 4 times its estimated height.
 
   \item The 1.3\,mm outer ring, that starts at $\sim$24\,au and has its peak intensity at $\sim$30\,au, presents a visible break in the surface brightness at $\sim$36\,au.
-***HOW IS THIS BREAK INTERPRETED IN THE RT**** ??
 
@@
 
-  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars.
-***IN LINE WITH PREVIOUS WORK**** except for ring6, comment on this and explain it.
+  \item Our parametric model, which accounts for the SED of the system, involves the existence of a sub-micron dust population close (<5\,au) to the stars, and predicts the presence of another inner ring at $\sim$5\,au made mainly of small dust grains.
+
+  \item The resolved radial width of Ring13 speaks for the presence of a considerable level of turbulent viscosity. ***SHOULD SAY HOW MUCH ***
 
@@
 
-This research has made use of the NASA/IPAC Infrared Science Archive, which is funded by the National Aeronautics and Space Administration and operated by the California Institute of Technology.
+This research has made use of the NASA/IPAC Infrared Science Archive,
+which is funded by the National Aeronautics and Space Administration
+and operated by the California Institute of Technology.
+S.C. acknowledges support from FONDECYT grant 1171624.
+S.P. acknowledges support from the Joint Committee of ESO and the
+Government of Chile and FONDECYT grant 1191934.
 
